---
title: "Data Centers & Local Economic Impact"
output: html_document
---

```{r setup, include=FALSE}
# ─── Libraries ─────────────────────────────────────────────────────────────────
library(knitr)       # R Markdown table rendering via kable()
library(tidyverse)   # Data wrangling (dplyr, tidyr, readr) + ggplot2 plotting
library(sf)          # Spatial vector data: reading, transforming, joining geometries
library(leaflet)     # Interactive HTML maps (pan, zoom, click, hover)
library(ggplot2)     # Grammar-of-graphics static plots
library(plotly)      # Converts ggplot2 objects → interactive HTML charts
library(tigris)      # Downloads US Census TIGER/Line county/state shapefiles
library(tidycensus)  # High-level Census API wrapper (ACS, Decennial)
library(censusapi)   # Lower-level Census API wrapper — used here for County Business Patterns
library(here)        # Constructs file paths relative to the project root (.Rproj)
library(did)         # Callaway & Sant'Anna (2021) staggered DiD estimator
library(ggpubr)      # Arranges multiple ggplots side-by-side (ggarrange)

# ─── Global Options ────────────────────────────────────────────────────────────
options(tigris_use_cache = TRUE)        # Cache downloaded TIGER shapefiles to avoid re-downloading

# I need to store Census API key in .Renviron, not in the code
# Run: usethis::edit_r_environ()  and add the line: CENSUS_KEY=your_key_here
Sys.setenv(CENSUS_KEY = Sys.getenv("CENSUS_KEY"))

knitr::opts_chunk$set(
  echo      = TRUE,
  tidy      = TRUE,
  tidy.opts = list(width.cutoff = 60),
  comment   = NA,
  fig.path  = "./figures/",
  fig.align = "center",
  fig.width = 9,
  fig.height = 5,
  message   = FALSE,
  warning   = FALSE
)
```

## Section 1: Geography: Defining the main land US

We restrict the analysis to the lower 48 contiguous states. Alaska and Hawaii have
very different economies and are spatially disconnected; US territories are not covered
by County Business Patterns data.

```{r}
# FIPS codes for non-contiguous states and US territories to exclude.
# 02 = Alaska, 15 = Hawaii, 60 = American Samoa, 66 = Guam,
# 69 = Northern Mariana Islands, 72 = Puerto Rico, 78 = US Virgin Islands
non_contiguous_fips <- c("02", "15", "60", "66", "69", "72", "78")

# Download county-level polygon boundaries from the Census TIGER/Line files.
# cb = TRUE requests the simplified "cartographic boundary" version — smaller file,
# loads faster, sufficient for county-level choropleth maps.
us_counties <- counties(cb = TRUE, year = 2023)

# Filter to lower 48 and reproject to WGS84 (EPSG:4326) — standard for web maps.
lower_48_counties <- us_counties %>%
  filter(!STATEFP %in% non_contiguous_fips) %>%
  st_transform(crs = 4326)
```


## Section 2: Data Centers, Load and Spatialize

```{r}
# Read the cleaned data center CSV.
# here() resolves the path relative to the project root so the script works
# on any machine regardless of the user's working directory.
# We keep only "Operational" facilities planned or under-construction sites
# have not yet produced any economic effects.
data_centers <- read.csv(here("data", "data_final", "economyDataFinal", "clean01EconDatacenter.csv")) %>%
  filter(stage == "Operational") %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
```

## Section 3: Treatment Assignment

 **Why 2007?**
> Amazon Web Services launched in 2006 and the large-scale commercial cloud computing
> era began in 2007. This triggered a wave of data center construction that continues
> today. Counties that received their first data center in 2007 or later are the
> **treatment group**.
> Counties that already had data centers before 2007 (perhaps even more recent than 2007?) are excluded because we cannot observe their pre-treatment period within our data.

```{r}
#Spatial join
# We place each data center inside the county it geographically belongs to.
# st_within (not st_intersects) avoids double-counting facilities that sit exactly
# on a county border.
# But then are we not missing data centers in independent cities?
data_centers_county <- st_join(
  data_centers,
  lower_48_counties,
  join = st_within
)

# County-level treatment classification
# Collapse from data-center level to county level.
# A county may host multiple data centers; we need a single status per county.
# County-level treatment classification
# Collapse from data-center level to county level.
# A county may host multiple data centers; we need one treatment status per county.

county_status <- data_centers_county %>%
  st_drop_geometry() %>%
  group_by(GEOID) %>%
  summarize(
    has_known_year = any(!is.na(year_operational)),

    earliest_known_year = if_else(
      has_known_year,
      min(year_operational, na.rm = TRUE),
      NA_real_
    ),

    .groups = "drop"
  ) %>%
  mutate(
    status = case_when(
      !has_known_year ~ "Drop: Missing Years",
      earliest_known_year < 2007 ~ "Drop: Pre-2007 Only",
      earliest_known_year >= 2007 ~ "Treated"
    ),

    first_dc_year = case_when(
      status == "Treated" ~ earliest_known_year,
      TRUE ~ NA_real_
    )
  )
```

```{r}
# Join status back onto the full county polygon dataset.
# Counties with no data centers at all receive status = "Control".
mapping_data <- lower_48_counties %>%
  left_join(
    county_status %>% select(GEOID, status, first_dc_year),
    by = "GEOID"
  ) %>%
  mutate(
    status = replace_na(status, "Control"),
    # Control counties have no treatment year, assign NA explicitly for clarity.
    first_dc_year = replace_na(first_dc_year, NA_real_)
  )
```


## Section 4: Interactive Map

> The map below shows each county color-coded by its treatment status.

**Notes:**
> 
- Are treated counties geographically clustered? Heavy clustering near
  tech hubs (Northern Virginia, Silicon Valley) is expected, but if all treated
  counties are in a handful of metro areas, generalizability of results will be limited.
- Are there large contiguous blocks of control counties that look plausibly
  similar to treated counties?
- Do any data center dots fall outside county polygons (into water or borders)?
  That would signal coordinate errors in the source data.

```{r}
status_palette <- colorFactor(
  palette = c("green", "grey", "orange", "red"),
  levels  = c("Treated", "Control", "Drop: Pre-2007 Only", "Drop: Missing Years")
)

leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron, group = "Base Map") %>%
  addPolygons(
    data        = mapping_data,
    fillColor   = ~status_palette(status),
    fillOpacity = 0.6,
    color       = "black",
    weight      = 1,
    label       = ~paste0(NAMELSAD, " — ", status),
    group       = "County Boundaries"
  ) %>%
  addCircleMarkers(
    data        = data_centers,
    color       = "black",
    weight      = 1,
    radius      = 3,
    fillOpacity = 1,
    label       = ~name,
    group       = "Data Centers"
  ) %>%
  addLegend(
    pal    = status_palette,
    values = c("Treated", "Control", "Drop: Pre-2007 Only", "Drop: Missing Years"),
    title  = "County Group"
  ) %>%
  addLayersControl(
    overlayGroups = c("Data Centers", "County Boundaries"),
    options       = layersControlOptions(collapsed = FALSE)
  )
```


## Section 5: Sample Size Tables

```{r sample-tables}
# Full breakdown of all county groups: it tells how many counties are excluded and why.
# A very large "Drop: Missing Years" group would probably be a red flag as it means many data centers have unknown opening years. But 254 does not seem very large compared to the other numbers 

status_summary <- mapping_data %>%
  st_drop_geometry() %>%
  mutate(
    status = factor(
      status,
      levels = c("Treated", "Control", "Drop: Pre-2007 Only", "Drop: Missing Years")
    )
  ) %>%
  count(status, name = "Count") %>%
  bind_rows(tibble(status = "Total", Count = sum(.$Count)))

kable(status_summary, caption = "County Counts by Status")

# Analysis sample only (the counties that go into regressions, aka treated and control).
analysis_summary <- mapping_data %>%
  st_drop_geometry() %>%
  filter(status %in% c("Treated", "Control")) %>%
  count(status, name = "Count") %>%
  bind_rows(tibble(status = "Total Analysis Sample", Count = sum(.$Count)))

kable(analysis_summary, caption = "Final Analysis Sample (Treated + Control Only)")
```


## Section 6: Data Center Opening Year Distribution

```{r}
# Count facilities by opening year.
year_counts <- data_centers %>%
  st_drop_geometry() %>%
  filter(!is.na(year_operational)) %>%
  count(year_operational)

p <- ggplot(
  year_counts,
  aes(
    x    = year_operational,
    y    = n,
    text = paste0("<span style='font-size:12px;'>Year: ", year_operational,
                  "<br>Centers: ", n, "</span>")
  )
) +
  geom_col(fill = "steelblue") +
  # Red dashed line marks the treatment cutoff year.
  geom_vline(xintercept = 2007, color = "red", linetype = "dashed", linewidth = 1) +
  annotate("text", x = 2007, y = max(year_counts$n),
           label = "Treatment cutoff (2007)", color = "red", hjust = -0.05) +
  scale_x_continuous(
    breaks = seq(min(year_counts$year_operational),
                 max(year_counts$year_operational), by = 1)
  ) +
  labs(title = "Data Centers Opened by Year", x = "Opening Year", y = "Number of Centers") +
  theme_minimal()

# What this chart tells us:
# - Is there a visible "boom" in openings after 2007? That would support the
#   hypothesis that cloud computing triggered construction. However, there seem to be a "boom" before 2007, but that can be explain by the fact that we are missing a couple of opening year? 
# - There are many openings before 2007, and those counties are dropped from the analysis. Is that okay?

ggplotly(p, tooltip = "text")
```


## Section 7: Pull County Business Patterns (CBP) Data

> For our report: 

> County Business Patterns is an annual Census survey reporting employment, payroll,
and establishment counts at the county level. It is the standard dataset for
county-level labor market analysis. We pull:
> 
- All industries combined:  the overall economic footprint
- NAICS 51 (Information): the sector data centers directly belong to
- NAICS 23 (Construction): construction jobs from building the facilities
- NAICS 54 (Professional/Scientific/Technical Services): downstream spillovers
- NAICS 22 (Utilities): power sector impacts (data centers are enormous energy consumers)
- More?

> Why start in 2002?

> We need pre-treatment observations to check that treated and control counties were
on similar trajectories before 2007 (the "parallel trends" assumption). Starting
in 2002 gives us roughly 5 pre-treatment years?  If the lines look parallel from
2002–2006, we have more confidence that post-2007 divergence is caused by data
centers rather than pre-existing differences.


```{r pull-cbp, cache=TRUE}
# Helper function to pull one year of CBP data for a given NAICS sector.
# naics = NULL pulls all-industry totals.
# We cache this chunk (cache=TRUE) because the API call takes several minutes.
pull_cbp_year <- function(yr, naics = NULL) {
  base_vars <- c("GEO_ID", "EMP", "PAYANN", "ESTAB")

  api_args <- list(
    name     = "cbp",
    vintage  = yr,
    vars     = base_vars,
    region   = "county:*",
    regionin = "state:*"
  )

  if (!is.null(naics)) {
    naics_var <- if (yr >= 2017) "NAICS2017" else if (yr >= 2008) "NAICS2007" else "NAICS2002"
    api_args[[naics_var]] <- naics
  }

  df <- tryCatch(
    do.call(getCensus, api_args),
    error = function(e) {
      message("Failed: year=", yr, " naics=", naics, ": ", e$message)
      return(NULL)
    }
  )

  if (is.null(df)) return(NULL)
  df$year        <- yr
  df$naics_group <- if (is.null(naics)) "All Industries" else paste0("NAICS ", naics)
  df
}
# ── Pull all-industry totals for 2003–2023 ─────────────────────────────────────
years <- 2003:2023

cbp_all <- bind_rows(lapply(years, pull_cbp_year, naics = NULL))

# ── Pull sector-specific data for key NAICS codes ─────────────────────────────
# These sectors are expected to be most directly affected by data center presence.
naics_sectors <- c(
  "51",   # Information — data centers are classified here
  "23",   # Construction — building the facilities
  "54",   # Professional/Scientific/Technical Services — knowledge spillovers
  "22"    # Utilities — power sector impact
)

cbp_sectors <- bind_rows(
  lapply(naics_sectors, function(naics) {
    bind_rows(lapply(years, pull_cbp_year, naics = naics))
  })
)

# Verify year coverage before proceeding
cbp_sectors %>%
  count(naics_group, year) %>%
  group_by(naics_group) %>%
  summarize(min_year = min(year), max_year = max(year), n_years = n_distinct(year))

# Combine all-industry and sector pulls into one long dataset
cbp_raw <- bind_rows(cbp_all, cbp_sectors)
```

```{r}
# Construct the 5-digit county GEOID (state FIPS + county FIPS).
# This matches the GEOID format in the spatial county data for joining.
# To verify we can use this example: state "51" + county "019" → GEOID "51019" (Montgomery County, VA)
cbp_clean <- cbp_raw %>%
  mutate(
    GEOID  = paste0(state, county),
    EMP    = as.numeric(EMP),
    PAYANN = as.numeric(PAYANN),
    ESTAB  = as.numeric(ESTAB)
  )
```



## Section 8: Validate the CBP Pull

```{r}
cat("Rows:", nrow(cbp_clean), "\n")
cat("Years covered:", min(cbp_clean$year), "–", max(cbp_clean$year), "\n")
cat("NAICS groups:", paste(unique(cbp_clean$naics_group), collapse = ", "), "\n\n")

#Check for completely missing values
na_summary <- cbp_clean %>%
  summarize(
    pct_missing_EMP    = mean(is.na(EMP))    * 100,
    pct_missing_PAYANN = mean(is.na(PAYANN)) * 100,
    pct_missing_ESTAB  = mean(is.na(ESTAB))  * 100
  )
cat("Missing value rates (%):\n")
print(na_summary) # currently I got null, which is good!


if (any(na_summary > 10)) {
  warning("More than 10% of values are missing in at least one variable.")
}

# ── Check for implausible zeros ────────────────────────────────────────────────
# CBP suppresses data for counties where reporting would reveal individual firms
# (confidentiality). These appear as EMP = 0 or very small values.
# For the all-industry total, a county with EMP = 0 almost certainly has
# suppressed data, not truly zero employment.
zero_emp <- cbp_clean %>%
  filter(naics_group == "All Industries", EMP == 0) %>%
  nrow()
cat("\nCounty-years with EMP = 0 (all industries):", zero_emp, "\n") #503

# Distribution check
# Print a quick summary of the three key variables (all-industry, most recent year).
cat("\nDistribution of key variables (All Industries, most recent year):\n")
cbp_clean %>%
  filter(naics_group == "All Industries", year == max(year)) %>%
  select(EMP, PAYANN, ESTAB) %>%
  summary() %>%
  print()

# We have some extreme maximum values > 2,000,000 but that most likely reflect large metro counties 

cbp_clean %>%
  filter(EMP < 0 | PAYANN < 0 | ESTAB < 0) %>%
  nrow() %>%
  cat("Rows with negative values:", ., "\n") # no negative values, which is good
```

## Section 9: Inflation Adjustment

Annual payroll (`PAYANN`) is in *nominal* dollars, it is not adjusted for inflation. We deflate to **2017 constant dollars** using the
CPI-U (Consumer Price Index for All Urban Consumers).

> The deflation factors below come from the Bureau of Labor Statistics CPI-U annual
> averages.

```{r}
# CPI-U annual averages (Base: 2017 = 100).
# Source: BLS CPI-U, All Items, Annual Average, Series CUUR0000SA0
# https://www.bls.gov/cpi/
cpi_u <- tibble(
  year = 2002:2023,
  cpi  = c(
    179.9,  # 2002
    184.0,  # 2003
    188.9,  # 2004
    195.3,  # 2005
    201.6,  # 2006
    207.3,  # 2007
    215.3,  # 2008
    214.5,  # 2009
    218.1,  # 2010
    224.9,  # 2011
    229.6,  # 2012
    233.0,  # 2013
    236.7,  # 2014
    237.0,  # 2015
    240.0,  # 2016
    245.1,  # 2017  ← base year (100)
    251.1,  # 2018
    255.7,  # 2019
    258.8,  # 2020
    270.9,  # 2021
    292.7,   # 2022
    304.7   # 2023
    
  )
)

# Compute the deflation factor for each year relative to the 2017 base.
# deflator = CPI_2017 / CPI_year
# Multiplying nominal values by the deflator converts them to 2017 constant dollars.
cpi_base <- cpi_u$cpi[cpi_u$year == 2017]

cpi_u <- cpi_u %>%
  mutate(deflator = cpi_base / cpi)

# Join deflators onto CBP data and compute real payroll.
cbp_real <- cbp_clean %>%
  left_join(cpi_u, by = "year") %>%
  mutate(
    # PAYANN_REAL: payroll in 2017 constant dollars
    # PAYANN is in $1,000s so the unit of PAYANN_REAL is also $1,000s (2017 dollars).
    PAYANN_REAL = PAYANN * deflator
  )
```



## Section 10: Merge with Treatment Status

```{r}
# Pull treatment status and first data center year for analysis counties only.
# We drop "Drop" categories here as they are ambiguous and cannot be cleanly
# assigned to treatment or control.
analysis_counties <- mapping_data %>%
  st_drop_geometry() %>%
  filter(status %in% c("Treated", "Control")) %>%
  select(GEOID, status, first_dc_year)

# Join CBP panel onto analysis counties.
# filter(!is.na(status)) removes CBP rows for counties that were dropped.
cbp_analysis <- cbp_real %>%
  left_join(analysis_counties, by = "GEOID") %>%
  filter(!is.na(status)) %>%
  # Replace suppressed zeros with NA so they don't drag down medians.
  mutate(
    EMP    = if_else(EMP    == 0, NA_real_, EMP),
    PAYANN = if_else(PAYANN == 0, NA_real_, PAYANN),
    PAYANN_REAL = if_else(PAYANN_REAL == 0, NA_real_, PAYANN_REAL),
    ESTAB  = if_else(ESTAB  == 0, NA_real_, ESTAB)
  )
```

## Section 10b: ACS data 

```{r acs-data, cache=TRUE}
acs_years <- 2009:2023

pull_acs_year <- function(yr) {

  if (yr <= 2018) {
    vars <- c(
      median_income = "DP03_0062",
      unemployment_rate = "DP03_0009P",
      pct_bachelors = "DP02_0061P",
      pct_hs_grad = "DP02_0067P",
      total_pop = "B01003_001"
    )
  } else {
    vars <- c(
      median_income = "DP03_0062",
      unemployment_rate = "DP03_0009P",
      pct_bachelors = "DP02_0062P",
      pct_hs_grad = "DP02_0068P",
      total_pop = "B01003_001"
    )
  }

  get_acs(
    geography = "county",
    variables = vars,
    year = yr,
    survey = "acs5"
  ) %>%
    mutate(year = yr)
}

acs_raw <- bind_rows(lapply(acs_years, pull_acs_year))

acs_covariates <- acs_raw %>%
  select(GEOID, year, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate) %>%
  mutate(
    log_pop = log(total_pop),
    log_median_income = log(median_income)
  ) %>%
  select(
    GEOID,
    year,
    log_pop,
    log_median_income,
    unemployment_rate,
    pct_hs_grad,
    pct_bachelors
  )

cbp_analysis_acs <- cbp_analysis %>%
  left_join(acs_covariates, by = c("GEOID", "year")) %>%
  filter(year >= 2009)

cat("Rows in ACS-matched analysis panel:", nrow(cbp_analysis_acs), "\n")

cbp_analysis_acs %>%
  filter(naics_group == "All Industries") %>%
  summarize(
    missing_log_pop = mean(is.na(log_pop)) * 100,
    missing_income = mean(is.na(log_median_income)) * 100,
    missing_unemployment = mean(is.na(unemployment_rate)) * 100,
    missing_hs = mean(is.na(pct_hs_grad)) * 100,
    missing_bs = mean(is.na(pct_bachelors)) * 100
  ) %>%
  print()
```

## Section 14: Staggered DiD Estimation
> Y_ct = β · D_ct + α_c + δ_t + ε_ct

```{r}
# Helper function: run full C&S DiD for any outcome variable
run_did <- function(outcome_var, outcome_label, data) {

  df <- data %>%
    filter(naics_group == "All Industries") %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    mutate(
      county_id = as.integer(factor(GEOID)),
      G = if_else(
        status == "Treated" & !is.na(first_dc_year),
        as.integer(first_dc_year),
        0L
      ),
      outcome = log(.data[[outcome_var]])
    )

  cs <- att_gt( yname = "outcome", tname = "year", idname = "county_id", gname = "G", data = df, control_group = "nevertreated", est_method = "reg", clustervars = "county_id", )

  att_overall <- aggte(cs, type = "simple")
  att_cal <- aggte(cs, type = "calendar")
  att_dyn <- aggte(cs, type = "dynamic")

  p_cal <- ggdid(att_cal) +
    labs(
      title = paste("Calendar Year Effects —", outcome_label),
      subtitle = "Callaway & Sant'Anna DiD | Never-treated controls",
      x = "Calendar Year",
      y = paste0("ATT (log ", outcome_label, ")")
    )

  p_event <- ggdid(att_dyn) + geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") + labs(
      title = paste("Event Study —", outcome_label), subtitle = "Red line = treatment onset", x = "Years Relative to First Data Center Opening", y = paste0("ATT (log ", outcome_label, ")"))

  list( label = outcome_label, cs = cs, overall = att_overall, calendar = att_cal, dynamic = att_dyn, p_cal = p_cal, p_event = p_event
  )
}

#  Run for each outcome
outcomes <- list(
  list(var = "EMP",         label = "Employment"),
  list(var = "PAYANN_REAL", label = "Real Annual Payroll (2017 $)"),
  list(var = "ESTAB",       label = "Establishments")
)

did_results <- lapply(outcomes, function(o) {
  run_did(
    outcome_var   = o$var,
    outcome_label = o$label,
    data          = cbp_analysis
  )
})

# Name the list
names(did_results) <- c("employment", "payroll", "establishments")


#  Access individual plots 
did_results$employment$p_event
did_results$payroll$p_event
did_results$establishments$p_event

```
## section DID cutoff date 2012 without controls
```{r did-cutoff-2012-no-controls}
run_did_2012 <- function(outcome_var, outcome_label, data) {
  df <- data %>%
    filter(naics_group == "All Industries") %>%
    filter(status == "Control" | (status == "Treated" & first_dc_year >= 2012 & first_dc_year <= 2020)) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    mutate(county_id = as.integer(factor(GEOID)), G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year), 0L), outcome = log(.data[[outcome_var]]))

  cs <- att_gt(yname = "outcome", tname = "year", idname = "county_id", gname = "G", xformla = ~ 1, control_group = "nevertreated", clustervars = "county_id", data = df)

  att_overall <- aggte(cs, type = "simple")
  att_dyn <- aggte(cs, type = "dynamic")

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    coord_cartesian(ylim = c(-0.2, 0.25)) +
    labs(title = paste("Event Study —", outcome_label), subtitle = "2012–2020 cohorts | No controls", x = "Years Relative to First Data Center Opening", y = paste0("ATT (log ", outcome_label, ")"))

  list(label = outcome_label, cs = cs, overall = att_overall, dynamic = att_dyn, p_event = p_event)
}

did_results_2012 <- lapply(outcomes, function(o) {
  run_did_2012(outcome_var = o$var, outcome_label = o$label, data = cbp_analysis)
})
names(did_results_2012) <- c("employment", "payroll", "establishments")

did_results_2012$employment$p_event
did_results_2012$payroll$p_event
did_results_2012$establishments$p_event
```
## Section DID cutoff date 2012 without controls — Not-Yet-Treated
```{r did-cutoff-2012-no-controls-nyt}
run_did_2012_nyt <- function(outcome_var, outcome_label, data) {
  df <- data %>%
    filter(naics_group == "All Industries") %>%
    filter(status == "Control" | (status == "Treated" & first_dc_year >= 2012 & first_dc_year <= 2020)) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    mutate(county_id = as.integer(factor(GEOID)), G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year), 0L), outcome = log(.data[[outcome_var]]))

  cs <- att_gt(yname = "outcome", tname = "year", idname = "county_id", gname = "G", xformla = ~ 1, control_group = "notyettreated", clustervars = "county_id", data = df)

  att_overall <- aggte(cs, type = "simple")
  att_dyn <- aggte(cs, type = "dynamic")

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    coord_cartesian(ylim = c(-0.2, 0.25)) +
    labs(title = paste("Event Study —", outcome_label), subtitle = "2012–2020 cohorts | No controls | Not-yet-treated control", x = "Years Relative to First Data Center Opening", y = paste0("ATT (log ", outcome_label, ")"))

  list(label = outcome_label, cs = cs, overall = att_overall, dynamic = att_dyn, p_event = p_event)
}

did_results_2012_nyt <- lapply(outcomes, function(o) {
  run_did_2012_nyt(outcome_var = o$var, outcome_label = o$label, data = cbp_analysis)
})
names(did_results_2012_nyt) <- c("employment", "payroll", "establishments")

did_results_2012_nyt$employment$p_event
did_results_2012_nyt$payroll$p_event
did_results_2012_nyt$establishments$p_event
```
## section DID with ACS controls
```{r did-with-acs-controls}
run_did_acs <- function(outcome_var, outcome_label, data) {

  df <- data %>%
    filter(naics_group == "All Industries") %>%
      filter(status == "Control" | (status == "Treated" & first_dc_year >= 2012 & first_dc_year <= 2020)) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    filter(!is.na(log_pop), !is.na(log_median_income), !is.na(pct_bachelors)) %>%
    
    mutate(county_id = as.integer(factor(GEOID)), G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year), 0L),
      outcome = log(.data[[outcome_var]])
    )

  cs <- att_gt(yname = "outcome", tname = "year", idname = "county_id", gname = "G", xformla = ~ log_pop + log_median_income + pct_bachelors,
    control_group = "nevertreated",
    clustervars = "county_id",
    data = df,
  )

  att_overall <- aggte(cs, type = "simple")
  att_dyn <- aggte(cs, type = "dynamic")

  p_event <- ggdid(att_dyn) +
  geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
  coord_cartesian(ylim = c(-0.2, 0.25)) +
  labs(
      title = paste("ACS-Controlled Event Study —", outcome_label),
      subtitle = "2009–2020 sample | ACS controls included",
      x = "Years Relative to First Data Center Opening",
      y = paste0("ATT (log ", outcome_label, ")")
    )

  list(
    label = outcome_label,
    cs = cs,
    overall = att_overall,
    dynamic = att_dyn,
    p_event = p_event
  )
}

did_results_acs <- lapply(outcomes, function(o) {
  run_did_acs( outcome_var = o$var, outcome_label = o$label, data = cbp_analysis_acs)
})

names(did_results_acs) <- c("employment", "payroll", "establishments")

did_results_acs$employment$p_event
did_results_acs$payroll$p_event
did_results_acs$establishments$p_event

```

## Section DID with ACS controls — Not-Yet-Treated
```{r did-with-acs-controls-nyt}
run_did_acs_nyt <- function(outcome_var, outcome_label, data) {
  df <- data %>%
    filter(naics_group == "All Industries") %>%
    filter(status == "Control" | (status == "Treated" & first_dc_year >= 2012 & first_dc_year <= 2020)) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    filter(!is.na(log_pop), !is.na(log_median_income), !is.na(pct_bachelors)) %>%
    mutate(county_id = as.integer(factor(GEOID)), G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year), 0L), outcome = log(.data[[outcome_var]]))

  cs <- att_gt(yname = "outcome", tname = "year", idname = "county_id", gname = "G", xformla = ~ log_pop + log_median_income + pct_bachelors, control_group = "notyettreated", clustervars = "county_id", data = df)

  att_overall <- aggte(cs, type = "simple")
  att_dyn <- aggte(cs, type = "dynamic")

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    coord_cartesian(ylim = c(-0.2, 0.25)) +
    labs(title = paste("ACS-Controlled Event Study —", outcome_label), subtitle = "2009–2020 sample | ACS controls | Not-yet-treated control", x = "Years Relative to First Data Center Opening", y = paste0("ATT (log ", outcome_label, ")"))

  list(label = outcome_label, cs = cs, overall = att_overall, dynamic = att_dyn, p_event = p_event)
}

did_results_acs_nyt <- lapply(outcomes, function(o) {
  run_did_acs_nyt(outcome_var = o$var, outcome_label = o$label, data = cbp_analysis_acs)
})
names(did_results_acs_nyt) <- c("employment", "payroll", "establishments")

did_results_acs_nyt$employment$p_event
did_results_acs_nyt$payroll$p_event
did_results_acs_nyt$establishments$p_event
```

## Section 15: Export Analysis Panel

```{r export}
# Save the final analysis panel to disk.
# This file contains one row per county × year × NAICS group,
# with treatment status, real payroll, log employment, and all CBP variables.
write_csv(
  cbp_analysis,
  here("data", "cbp_analysis_panel.csv")
)

```