---
title: "Data Centers & Light at Night: County-Level DiD Analysis"
author: ""
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(sf)
library(tigris)
library(readxl)
library(janitor)
library(here)
library(did)
library(tidycensus)

options(tigris_use_cache = TRUE)

# Let tidycensus find the key whether your project uses CENSUS_KEY or CENSUS_API_KEY.
if (Sys.getenv("CENSUS_API_KEY") == "" && Sys.getenv("CENSUS_KEY") != "") {
  Sys.setenv(CENSUS_API_KEY = Sys.getenv("CENSUS_KEY"))
}

knitr::opts_chunk$set(echo = TRUE, tidy = FALSE, comment = NA, fig.path = "./figures/", fig.align = "center", fig.width = 9, fig.height = 5, message = FALSE, warning = FALSE)

lights_start_year <- 2012
lights_end_year   <- 2020
lights_sheet <- "2020_boundary_ALAN_2012_to_2020"
lights_file <- here("data", "data_raw", "ALAN_VIIRS_CONUS_2012_to_2020_county_level.xlsx")
data_centers_file <- here("data", "data_final", "economyDataFinal", "clean01EconDatacenter.csv")
county_health_dir <- here("data", "economyData", "raw_migration")

print_all_event_plots <- TRUE

# Minimum treated counties required in a cohort after filtering to avoid extremely small treated cohorts that can make att_gt unstable.
min_treated_cohort_size <- 5

# Output folders.
dir.create(here("figures"), showWarnings = FALSE, recursive = TRUE)
dir.create(here("outputs"), showWarnings = FALSE, recursive = TRUE)
```

## Section 1: County Boundaries

Download lower-48 county polygons from Census TIGER/Line. These polygons are used
only to assign each data center to a county.

```{r county-boundaries}
non_contiguous_fips <- c("02", "15", "60", "66", "69", "72", "78")

lower_48_counties <- counties(cb = TRUE, year = 2020) %>%
  filter(!STATEFP %in% non_contiguous_fips) %>%
  st_transform(crs = 4326)

lower_48_counties %>%
  st_drop_geometry() %>%
  summarize(n_counties = n_distinct(GEOID))
```


## Section 2: Load Data Centers

Read the cleaned data center file and keep operational facilities with valid
coordinates.

```{r load-datacenters}
data_centers <- readr::read_csv(data_centers_file, show_col_types = FALSE) %>%
  mutate(longitude = as.numeric(longitude), latitude = as.numeric(latitude), year_operational = as.numeric(year_operational)) %>%
  filter(stage == "Operational", !is.na(longitude), !is.na(latitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
#glimpse(data_centers)
```

## Section 3: Treatment Assignment

A county is treated when its first operational data center appears during the
lights panel, 2012-2020. Counties with first data centers before 2012 are already
treated before the outcome panel starts, so they are dropped from the main DiD.
Counties with no data center during the observed lights panel are controls.

```{r treatment-assignment}
data_centers_county <- st_join(data_centers, lower_48_counties %>% select(GEOID, NAMELSAD, STATEFP, geometry), join = st_within)

county_status <- data_centers_county %>%
  st_drop_geometry() %>%
  filter(!is.na(GEOID)) %>%
  group_by(GEOID) %>%
  summarize(has_known_year = any(!is.na(year_operational)), earliest_known_year = if_else(has_known_year, min(year_operational, na.rm = TRUE), NA_real_), dc_count = n(), .groups = "drop") %>%
  mutate(
    status = case_when(
      !has_known_year ~ "Drop: Missing Years",
      earliest_known_year < lights_start_year ~ "Drop: Pre-2012",
      earliest_known_year <= lights_end_year ~ "Treated",
      TRUE ~ "Control"
    ),
    first_dc_year = if_else(status == "Treated", earliest_known_year, NA_real_)
  )

analysis_counties <- lower_48_counties %>%
  st_drop_geometry() %>%
  select(GEOID, county_name = NAMELSAD, STATEFP) %>%
  left_join(county_status %>% select(GEOID, status, first_dc_year, dc_count), by = "GEOID") %>%
  mutate(status = replace_na(status, "Control"), dc_count = replace_na(dc_count, 0L))

analysis_counties %>%
  count(status)

analysis_counties %>%
  filter(status == "Treated") %>%
  count(first_dc_year, name = "n_treated_counties") %>%
  arrange(first_dc_year)
```

## Section 4: Load County-Level VIIRS ALAN Data

```{r load-lights}
excel_sheets(lights_file)

lights_raw <- read_excel(lights_file, sheet = lights_sheet) %>%
  clean_names()

glimpse(lights_raw)

lights_county <- lights_raw %>%
  # county_id may be read as numeric, so leading zeroes need to be restored.
  mutate(GEOID = stringr::str_pad(as.character(as.integer(as.numeric(county_id))), 5, pad = "0"), year = as.integer(year), across(starts_with("rad_"), as.numeric), nraster = as.numeric(nraster)) %>%
  filter(year >= lights_start_year, year <= lights_end_year) %>%
  select(GEOID, county_id, county, state, year, nraster, rad_mean, rad_min, rad_max, rad_median, rad_sd, rad_q25, rad_q75, rad_iqr)
#glimpse(lights_county)

lights_county %>%
  summarize(years = paste(sort(unique(year)), collapse = ", "), n_counties = n_distinct(GEOID), n_county_years = n())
```

## Section 5: Merge Lights With Treatment Status
Each county-year light observation gets the county's treatment status, first data center year, and datacenter count.

```{r merge-lights-treatment}
lights_analysis <- lights_county %>%
  inner_join(analysis_counties %>% select(GEOID, status, first_dc_year, dc_count), by = "GEOID") %>%
  filter(status %in% c("Treated", "Control")) %>%
  # Radiance measures should not be negative. Any negative values are treated as missing.
  mutate(across(starts_with("rad_"), ~ if_else(.x < 0, NA_real_, .x)))

#glimpse(lights_analysis)

lights_analysis %>%
  count(status, year) %>%
  pivot_wider(names_from = status, values_from = n)
```


## Section 6: ACS + County Health Covariates

These covariates are used only in the covariate-controlled specifications. They
are lagged one year so the controls are measured before the light outcome year.
For example, the 2012 light outcome uses 2011 controls, and the 2020 light outcome uses 2019 controls.

The Census/ACS pull gives population, income, and education controls. The County
Health files add race-share controls, matching the extra covariates used in the
economic-impact analysis.

```{r acs-county-health-covariates}
acs_years <- (lights_start_year - 1):(lights_end_year - 1)

pull_acs_year <- function(yr) {
  base_vars <- c(median_income = "DP03_0062", pct_bachelors = if (yr <= 2018) "DP02_0061P" else "DP02_0062P", pct_hs_grad = if (yr <= 2018) "DP02_0067P" else "DP02_0068P", total_pop = "B01003_001")

  get_acs(geography = "county", variables = base_vars, year = yr, survey = "acs5", cache_table = TRUE) %>%
    select(GEOID, variable, estimate) %>%
    pivot_wider(names_from = variable, values_from = estimate) %>%
    mutate(acs_year = yr, log_pop = log(total_pop), log_median_income = log(median_income))
}

read_county_health_year <- function(yr) {
  county_health_file <- file.path(county_health_dir, paste0("clh_", yr, "_county_2_0.xlsx"))

  if (!file.exists(county_health_file)) {
    warning("Missing County Health file: ", county_health_file)
    return(tibble(GEOID = character(), ch_year = integer(), ACS_PCT_WHITE = numeric(), ACS_PCT_BLACK = numeric(), ACS_PCT_HISPANIC = numeric(), ACS_PCT_ASIAN = numeric(), ACS_PCT_AIAN = numeric()))
  }

  read_excel(county_health_file, sheet = "Data", col_types = "text") %>%
    transmute(
      GEOID = str_pad(as.character(COUNTYFIPS), 5, pad = "0"),
      ch_year = as.integer(YEAR),
      ACS_PCT_WHITE = as.numeric(ACS_PCT_WHITE),
      ACS_PCT_BLACK = as.numeric(ACS_PCT_BLACK),
      ACS_PCT_HISPANIC = as.numeric(ACS_PCT_HISPANIC),
      ACS_PCT_ASIAN = as.numeric(ACS_PCT_ASIAN),
      ACS_PCT_AIAN = as.numeric(ACS_PCT_AIAN)
    )
}

acs_covariates <- bind_rows(lapply(acs_years, pull_acs_year))
county_health_covariates <- bind_rows(lapply(acs_years, read_county_health_year))

acs_lagged <- acs_covariates %>%
  transmute(GEOID, year = acs_year + 1L, lag_log_pop = log_pop, lag_log_median_income = log_median_income, lag_pct_bachelors = pct_bachelors, lag_pct_hs_grad = pct_hs_grad)

county_health_lagged <- county_health_covariates %>%
  transmute(GEOID, year = ch_year + 1L, lag_pct_white = ACS_PCT_WHITE, lag_pct_black = ACS_PCT_BLACK, lag_pct_hispanic = ACS_PCT_HISPANIC, lag_pct_asian = ACS_PCT_ASIAN, lag_pct_aian = ACS_PCT_AIAN) %>%
  distinct(GEOID, year, .keep_all = TRUE)

lights_analysis_acs <- lights_analysis %>%
  left_join(acs_lagged, by = c("GEOID", "year")) %>%
  left_join(county_health_lagged, by = c("GEOID", "year"))

did_control_vars <- c("lag_log_pop", "lag_log_median_income", "lag_pct_bachelors", "lag_pct_hs_grad", "lag_pct_white", "lag_pct_black", "lag_pct_hispanic", "lag_pct_asian", "lag_pct_aian")
did_control_formula <- as.formula(paste("~", paste(did_control_vars, collapse = " + ")))

glimpse(lights_analysis_acs)

lights_analysis_acs %>%
  summarize(across(all_of(did_control_vars), ~ sum(is.na(.x)), .names = "missing_{.col}"))
```

## Section 7: Outcome List and Model Grid

`nraster` is not treated as a light outcome because it is the number of raster
pixels in the county, which mostly reflects county size/coverage. The regression
outcomes are the available `rad_` variables.

```{r outcome-and-model-grid}
light_outcomes <- tibble::tribble(
  ~outcome_var, ~outcome_label, ~outcome_type,
  "rad_mean",   "Mean Radiance",                "average intensity",
  "rad_min",    "Minimum Radiance",             "lower tail / darkest pixel",
  "rad_max",    "Maximum Radiance",             "brightest pixel / hotspot",
  "rad_median", "Median Radiance",              "typical pixel",
  "rad_sd",     "Radiance Standard Deviation",  "within-county dispersion",
  "rad_q25",    "25th Percentile Radiance",     "lower quartile",
  "rad_q75",    "75th Percentile Radiance",     "upper quartile",
  "rad_iqr",    "Radiance Interquartile Range", "middle-spread dispersion"
)

model_specs <- tibble::tribble(
  ~spec_id,    ~control_group,  ~use_covariates, ~spec_label,
  "nt_nocov",  "nevertreated",  FALSE,           "Never Treated | No Covariates",
  "nyt_nocov", "notyettreated", FALSE,           "Not Yet Treated | No Covariates",
  "nt_cov",    "nevertreated",  TRUE,            "Never Treated | Lagged ACS + Race Covariates",
  "nyt_cov",   "notyettreated", TRUE,            "Not Yet Treated | Lagged ACS + Race Covariates"
)

model_grid <- tidyr::crossing(light_outcomes, model_specs) %>%
  mutate(model_id = paste(outcome_var, spec_id, sep = "__"))

knitr::kable(model_grid, caption = "Nighttime Lights Outcome x DiD Specification Grid")
```

## Section 8: DiD Function

All outcomes are transformed using `log1p(x) = log(1 + x)`. This keeps zero-light
observations instead of dropping them. The interpretation is approximately a
percentage change for small-to-moderate effects, but the exact interpretation is a
change in log one-plus radiance.

```{r did-function}
run_lights_did <- function(outcome_var, outcome_label, outcome_type, control_group, use_covariates, spec_label, data, transform = "log1p", min_cohort_size = min_treated_cohort_size, start_year = lights_start_year, end_year = lights_end_year) {

  n_years <- length(start_year:end_year)

  control_vars <- did_control_vars

  df <- data %>%
    filter(status == "Control" | (status == "Treated" & first_dc_year >= start_year & first_dc_year <= end_year)) %>%
    filter(year >= start_year, year <= end_year) %>%
    mutate(outcome_raw = .data[[outcome_var]]) %>%
    filter(!is.na(outcome_raw), outcome_raw >= 0)

  if (use_covariates) {
    df <- df %>% filter(if_all(all_of(control_vars), ~ !is.na(.x)))
    xformla <- did_control_formula
    covariate_label <- "Lagged ACS + race covariates"
  } else {
    xformla <- ~ 1
    covariate_label <- "No covariates"
  }

  df <- df %>%
    group_by(GEOID) %>%
    filter(n_distinct(year) == n_years) %>%
    ungroup() %>%
    mutate(G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year), 0L)) %>%
    group_by(G) %>%
    filter(G == 0 | n_distinct(GEOID) >= min_cohort_size) %>%
    ungroup() %>%
    mutate(county_id_did = as.integer(factor(GEOID)))

  if (transform == "log1p") {
    df <- df %>% mutate(outcome = log1p(outcome_raw))
    y_label <- paste0("ATT (log(1 + ", outcome_label, "))")
  } else if (transform == "log") {
    df <- df %>% filter(outcome_raw > 0) %>% mutate(outcome = log(outcome_raw))
    y_label <- paste0("ATT (log ", outcome_label, ")")
  } else if (transform == "level") {
    df <- df %>% mutate(outcome = outcome_raw)
    y_label <- paste0("ATT (", outcome_label, ")")
  } else {
    stop("transform must be one of: 'log1p', 'log', or 'level'.")
  }

  cohort_sizes <- df %>%
    filter(G > 0) %>%
    distinct(GEOID, G) %>%
    count(G, name = "n_treated_counties") %>%
    arrange(G)

  cs <- att_gt(yname = "outcome", tname = "year", idname = "county_id_did", gname = "G", xformla = xformla, control_group = control_group, clustervars = "county_id_did", allow_unbalanced_panel = TRUE, data = df)

  att_overall <- aggte(cs, type = "simple", na.rm = TRUE)
  att_dyn <- aggte(cs, type = "dynamic", na.rm = TRUE)
  att_cal <- aggte(cs, type = "calendar", na.rm = TRUE)

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    labs(title = paste("Event Study —", outcome_label), subtitle = paste0(start_year, "–", end_year, " cohorts | ", control_group, " control | ", covariate_label), x = "Years Relative to First Data Center Opening", y = y_label)

  p_calendar <- ggdid(att_cal) +
    labs(title = paste("Calendar-Time Effects —", outcome_label), subtitle = paste0(start_year, "–", end_year, " cohorts | ", control_group, " control | ", covariate_label), x = "Calendar year", y = y_label)

  list(error = FALSE, outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, transform = transform, data_used = df, cohort_sizes = cohort_sizes, cs = cs, overall = att_overall, dynamic = att_dyn, calendar = att_cal, p_event = p_event, p_calendar = p_calendar)
}

run_lights_did_safe <- function(outcome_var, outcome_label, outcome_type, control_group, use_covariates, spec_label, data) {
  tryCatch(
    run_lights_did(outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, data = data, transform = "log1p"),
    error = function(e) {
      list(error = TRUE, error_message = conditionMessage(e), outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, transform = "log1p")
    }
  )
}
```

## Section 9: Run All Light Outcome Regressions

```{r run-all-did}
set.seed(12345)
all_light_did_results <- pmap(
  model_grid,
  function(outcome_var, outcome_label, outcome_type, spec_id, control_group, use_covariates, spec_label, model_id) {
    run_lights_did_safe(outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, data = lights_analysis_acs)
  }
)
names(all_light_did_results) <- model_grid$model_id

# Check whether any models failed.
model_status <- tibble(model_id = names(all_light_did_results), error = map_lgl(all_light_did_results, "error"), error_message = map_chr(all_light_did_results, ~ { if (isTRUE(.x$error)) .x$error_message else "" }))

knitr::kable(model_status, caption = "Model Run Status")
```

---

## Section 10: Results Summary Table

```{r results-summary}


extract_lights_results <- function(result) {
  cg   <- dplyr::recode(result$control_group,
                        "nevertreated"  = "Never Treated",
                        "notyettreated" = "Not Yet Treated")
  spec <- if (result$use_covariates) "Lagged ACS + Race Controls" else "No Covariates"

  if (isTRUE(result$error)) {
    return(tibble(Outcome = result$outcome_label, `Outcome Variable` = result$outcome_var, `Outcome Type` = result$outcome_type, Specification = spec, `Control Group` = cg, Covariates = if_else(result$use_covariates, "Yes", "No"), Transform = result$transform, ATT = NA_real_, SE = NA_real_, `95% CI Lower` = NA_real_, `95% CI Upper` = NA_real_, `p-value` = NA_real_, `Counties Used` = NA_integer_, `County-Years Used` = NA_integer_, Status = "Error", `Error Message` = result$error_message))
  }

  ATT <- result$overall$overall.att
  SE <- result$overall$overall.se
  p_value <- 2 * (1 - pnorm(abs(ATT / SE)))

  tibble(Outcome = result$outcome_label, `Outcome Variable` = result$outcome_var, `Outcome Type` = result$outcome_type, Specification = result$spec_label, `Control Group` = result$control_group, Covariates = if_else(result$use_covariates, "Yes", "No"), Transform = result$transform, ATT = ATT, SE = SE, `95% CI Lower` = ATT - 1.96 * SE, `95% CI Upper` = ATT + 1.96 * SE, `p-value` = p_value, `Counties Used` = n_distinct(result$data_used$GEOID), `County-Years Used` = nrow(result$data_used), Status = "OK", `Error Message` = "")
}

lights_results_summary <- bind_rows(lapply(all_light_did_results, extract_lights_results)) %>%
  arrange(`Outcome Variable`, Covariates, `Control Group`)

knitr::kable(lights_results_summary, digits = 3, caption = "Overall ATT Estimates for All County-Level Artificial Light at Night Outcomes")

shiny_report_dir <- here::here("..", "..", "ShinyApp", "report")
dir.create(shiny_report_dir, showWarnings = FALSE, recursive = TRUE)

saveRDS(
  all_light_did_results,
  file.path(shiny_report_dir, "all_light_did_results.rds")
)

saveRDS(
  lights_results_summary,
  file.path(shiny_report_dir, "lights_results_summary.rds")
)

readr::write_csv(
  lights_results_summary,
  file.path(shiny_report_dir, "lights_results_summary.csv")
)

# Also export a copy for the Shiny app results table.
# If this Rmd is run from the repo root, ShinyApp/report is usually the correct target.
shiny_report_dir <- here("ShinyApp", "report")
if (!dir.exists(shiny_report_dir)) shiny_report_dir <- here("report")
dir.create(shiny_report_dir, showWarnings = FALSE, recursive = TRUE)
saveRDS(lights_results_summary, file.path(shiny_report_dir, "lights_results_summary.rds"))
```

## Section 11: Event Study Plots

This prints and saves event-study plots for every successful model when
`print_all_event_plots <- TRUE`.

```{r event-study-plots, eval=print_all_event_plots}
for (model_id in names(all_light_did_results)) {
  res <- all_light_did_results[[model_id]]
  if (isFALSE(res$error)) {
    print(res$p_event)
    ggsave(here("figures", paste0("event_study__", model_id, ".png")), res$p_event, width = 9, height = 5, dpi = 150)
  }
}
```

## Section 12: Descriptive Summary Data for Shiny or Reporting

```{r descriptive-summary-export}
lights_summary_data <- lights_analysis_acs %>%
  transmute(GEOID, county, state, year, status, first_dc_year, dc_count, nraster, rad_mean, rad_min, rad_max, rad_median, rad_sd, rad_q25, rad_q75, rad_iqr, across(all_of(did_control_vars)))

saveRDS(lights_summary_data, here("outputs", "lights_summary_data.rds"))

summary_tbl <- lights_summary_data %>%
  select(starts_with("rad_")) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "value") %>%
  filter(!is.na(value)) %>%
  group_by(Variable) %>%
  summarize(N = n(), Mean = mean(value), SD = sd(value), Min = min(value), Median = median(value), Max = max(value), .groups = "drop") %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))

knitr::kable(summary_tbl, caption = "Descriptive Summary of Light Outcomes")
```
