---
title: "Data Centers: Master Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

# Part I — Data Centers & Light at Night


```{r lights__setup, include=FALSE}
library(knitr)
library(tidyverse)
library(sf)
library(tigris)
library(readxl)
library(janitor)
library(here)
library(did)
library(tidycensus)

options(tigris_use_cache = TRUE)

# Let tidycensus find the key whether your project uses CENSUS_KEY or CENSUS_API_KEY.
if (Sys.getenv("CENSUS_API_KEY") == "" && Sys.getenv("CENSUS_KEY") != "") {
  Sys.setenv(CENSUS_API_KEY = Sys.getenv("CENSUS_KEY"))
}

knitr::opts_chunk$set(echo = TRUE, tidy = FALSE, comment = NA, fig.path = "./figures/", fig.align = "center", fig.width = 9, fig.height = 5, message = FALSE, warning = FALSE)

lights_start_year <- 2012
lights_end_year   <- 2020
lights_sheet <- "2020_boundary_ALAN_2012_to_2020"
lights_file <- here("data", "data_raw", "ALAN_VIIRS_CONUS_2012_to_2020_county_level.xlsx")
data_centers_file <- here("data", "data_final", "economyDataFinal", "clean01EconDatacenter.csv")
county_health_dir <- here("data", "economyData", "raw_migration")

print_all_event_plots <- TRUE

# Minimum treated counties required in a cohort after filtering to avoid extremely small treated cohorts that can make att_gt unstable.
min_treated_cohort_size <- 2

# Output folders.
dir.create(here("figures"), showWarnings = FALSE, recursive = TRUE)
dir.create(here("outputs"), showWarnings = FALSE, recursive = TRUE)
```

## Section 1: County Boundaries

Download lower-48 county polygons from Census TIGER/Line. These polygons are used
only to assign each data center to a county.

```{r lights__county-boundaries}
non_contiguous_fips <- c("02", "15", "60", "66", "69", "72", "78")

lower_48_counties <- counties(cb = TRUE, year = 2020) %>%
  filter(!STATEFP %in% non_contiguous_fips) %>%
  st_transform(crs = 4326)

lower_48_counties %>%
  st_drop_geometry() %>%
  summarize(n_counties = n_distinct(GEOID))
```


## Section 2: Load Data Centers

Read the cleaned data center file and keep operational facilities with valid
coordinates.

```{r lights__load-datacenters}
data_centers <- readr::read_csv(data_centers_file, show_col_types = FALSE) %>%
  mutate(longitude = as.numeric(longitude), latitude = as.numeric(latitude), year_operational = as.numeric(year_operational)) %>%
  filter(stage == "Operational", !is.na(longitude), !is.na(latitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
#glimpse(data_centers)
```

## Section 3: Treatment Assignment

A county is treated when its first operational data center appears during the
lights panel, 2012-2020. Counties with first data centers before 2012 are already
treated before the outcome panel starts, so they are dropped from the main DiD.
Counties with no data center during the observed lights panel are controls.

```{r lights__treatment-assignment}
data_centers_county <- st_join(data_centers, lower_48_counties %>% select(GEOID, NAMELSAD, STATEFP, geometry), join = st_within)

county_status <- data_centers_county %>%
  st_drop_geometry() %>%
  filter(!is.na(GEOID)) %>%
  group_by(GEOID) %>%
  summarize(has_known_year = any(!is.na(year_operational)), earliest_known_year = if_else(has_known_year, min(year_operational, na.rm = TRUE), NA_real_), dc_count = n(), .groups = "drop") %>%
  mutate(
    status = case_when(
      !has_known_year ~ "Drop: Missing Years",
      earliest_known_year < lights_start_year ~ "Drop: Pre-2012",
      earliest_known_year <= lights_end_year ~ "Treated",
      TRUE ~ "Control"
    ),
    first_dc_year = if_else(status == "Treated", earliest_known_year, NA_real_)
  )

analysis_counties <- lower_48_counties %>%
  st_drop_geometry() %>%
  select(GEOID, county_name = NAMELSAD, STATEFP) %>%
  left_join(county_status %>% select(GEOID, status, first_dc_year, dc_count), by = "GEOID") %>%
  mutate(status = replace_na(status, "Control"), dc_count = replace_na(dc_count, 0L))

analysis_counties %>%
  count(status)

analysis_counties %>%
  filter(status == "Treated") %>%
  count(first_dc_year, name = "n_treated_counties") %>%
  arrange(first_dc_year)
```

## Section 4: Load County-Level VIIRS ALAN Data

```{r lights__load-lights}
excel_sheets(lights_file)

lights_raw <- read_excel(lights_file, sheet = lights_sheet) %>%
  clean_names()

glimpse(lights_raw)

lights_county <- lights_raw %>%
  # county_id may be read as numeric, so leading zeroes need to be restored.
  mutate(GEOID = stringr::str_pad(as.character(as.integer(as.numeric(county_id))), 5, pad = "0"), year = as.integer(year), across(starts_with("rad_"), as.numeric), nraster = as.numeric(nraster)) %>%
  filter(year >= lights_start_year, year <= lights_end_year) %>%
  select(GEOID, county_id, county, state, year, nraster, rad_mean, rad_min, rad_max, rad_median, rad_sd, rad_q25, rad_q75, rad_iqr)
#glimpse(lights_county)

lights_county %>%
  summarize(years = paste(sort(unique(year)), collapse = ", "), n_counties = n_distinct(GEOID), n_county_years = n())
```

## Section 5: Merge Lights With Treatment Status
Each county-year light observation gets the county's treatment status, first data center year, and datacenter count.

```{r lights__merge-lights-treatment}
lights_analysis <- lights_county %>%
  inner_join(analysis_counties %>% select(GEOID, status, first_dc_year, dc_count), by = "GEOID") %>%
  filter(status %in% c("Treated", "Control")) %>%
  # Radiance measures should not be negative. Any negative values are treated as missing.
  mutate(across(starts_with("rad_"), ~ if_else(.x < 0, NA_real_, .x)))

#glimpse(lights_analysis)

lights_analysis %>%
  count(status, year) %>%
  pivot_wider(names_from = status, values_from = n)
```


## Section 6: ACS + County Health Covariates

These covariates are used only in the covariate-controlled specifications. They
are lagged one year so the controls are measured before the light outcome year.
For example, the 2012 light outcome uses 2011 controls, and the 2020 light outcome uses 2019 controls.

The Census/ACS pull gives population, income, and education controls. The County
Health files add race-share controls, matching the extra covariates used in the
economic-impact analysis.

```{r lights__acs-county-health-covariates}
acs_years <- (lights_start_year - 1):(lights_end_year - 1)

pull_acs_year <- function(yr) {
  base_vars <- c(median_income = "DP03_0062", pct_bachelors = if (yr <= 2018) "DP02_0061P" else "DP02_0062P", pct_hs_grad = if (yr <= 2018) "DP02_0067P" else "DP02_0068P", total_pop = "B01003_001")

  get_acs(geography = "county", variables = base_vars, year = yr, survey = "acs5", cache_table = TRUE) %>%
    select(GEOID, variable, estimate) %>%
    pivot_wider(names_from = variable, values_from = estimate) %>%
    mutate(acs_year = yr, log_pop = log(total_pop), log_median_income = log(median_income))
}

read_county_health_year <- function(yr) {
  county_health_file <- file.path(county_health_dir, paste0("clh_", yr, "_county_2_0.xlsx"))

  if (!file.exists(county_health_file)) {
    warning("Missing County Health file: ", county_health_file)
    return(tibble(GEOID = character(), ch_year = integer(), ACS_PCT_WHITE = numeric(), ACS_PCT_BLACK = numeric(), ACS_PCT_HISPANIC = numeric(), ACS_PCT_ASIAN = numeric(), ACS_PCT_AIAN = numeric()))
  }

  read_excel(county_health_file, sheet = "Data", col_types = "text") %>%
    transmute(
      GEOID = str_pad(as.character(COUNTYFIPS), 5, pad = "0"),
      ch_year = as.integer(YEAR),
      ACS_PCT_WHITE = as.numeric(ACS_PCT_WHITE),
      ACS_PCT_BLACK = as.numeric(ACS_PCT_BLACK),
      ACS_PCT_HISPANIC = as.numeric(ACS_PCT_HISPANIC),
      ACS_PCT_ASIAN = as.numeric(ACS_PCT_ASIAN),
      ACS_PCT_AIAN = as.numeric(ACS_PCT_AIAN)
    )
}

acs_covariates <- bind_rows(lapply(acs_years, pull_acs_year))
county_health_covariates <- bind_rows(lapply(acs_years, read_county_health_year))

acs_lagged <- acs_covariates %>%
  transmute(GEOID, year = acs_year + 1L, lag_log_pop = log_pop, lag_log_median_income = log_median_income, lag_pct_bachelors = pct_bachelors, lag_pct_hs_grad = pct_hs_grad)

county_health_lagged <- county_health_covariates %>%
  transmute(GEOID, year = ch_year + 1L, lag_pct_white = ACS_PCT_WHITE, lag_pct_black = ACS_PCT_BLACK, lag_pct_hispanic = ACS_PCT_HISPANIC, lag_pct_asian = ACS_PCT_ASIAN, lag_pct_aian = ACS_PCT_AIAN) %>%
  distinct(GEOID, year, .keep_all = TRUE)

lights_analysis_acs <- lights_analysis %>%
  left_join(acs_lagged, by = c("GEOID", "year")) %>%
  left_join(county_health_lagged, by = c("GEOID", "year"))

did_control_vars <- c("lag_log_pop", "lag_log_median_income", "lag_pct_bachelors", "lag_pct_hs_grad", "lag_pct_white", "lag_pct_black", "lag_pct_hispanic", "lag_pct_asian", "lag_pct_aian")
did_control_formula <- as.formula(paste("~", paste(did_control_vars, collapse = " + ")))

glimpse(lights_analysis_acs)

lights_analysis_acs %>%
  summarize(across(all_of(did_control_vars), ~ sum(is.na(.x)), .names = "missing_{.col}"))
```

## Section 7: Outcome List and Model Grid

`nraster` is not treated as a light outcome because it is the number of raster
pixels in the county, which mostly reflects county size/coverage. The regression
outcomes are the available `rad_` variables.

```{r lights__outcome-and-model-grid}
light_outcomes <- tibble::tribble(
  ~outcome_var, ~outcome_label, ~outcome_type,
  "rad_mean",   "Mean Radiance",                "average intensity",
  "rad_min",    "Minimum Radiance",             "lower tail / darkest pixel",
  "rad_max",    "Maximum Radiance",             "brightest pixel / hotspot",
  "rad_median", "Median Radiance",              "typical pixel",
  "rad_sd",     "Radiance Standard Deviation",  "within-county dispersion",
  "rad_q25",    "25th Percentile Radiance",     "lower quartile",
  "rad_q75",    "75th Percentile Radiance",     "upper quartile",
  "rad_iqr",    "Radiance Interquartile Range", "middle-spread dispersion"
)

model_specs <- tibble::tribble(
  ~spec_id,    ~control_group,  ~use_covariates, ~spec_label,
  "nt_nocov",  "nevertreated",  FALSE,           "Never Treated | No Covariates",
  "nyt_nocov", "notyettreated", FALSE,           "Not Yet Treated | No Covariates",
  "nt_cov",    "nevertreated",  TRUE,            "Never Treated | Lagged ACS + Race Covariates",
  "nyt_cov",   "notyettreated", TRUE,            "Not Yet Treated | Lagged ACS + Race Covariates"
)

model_grid <- tidyr::crossing(light_outcomes, model_specs) %>%
  mutate(model_id = paste(outcome_var, spec_id, sep = "__"))

knitr::kable(model_grid, caption = "Nighttime Lights Outcome x DiD Specification Grid")
```

## Section 8: DiD Function

All outcomes are transformed using `log1p(x) = log(1 + x)`. This keeps zero-light
observations instead of dropping them. The interpretation is approximately a
percentage change for small-to-moderate effects, but the exact interpretation is a
change in log one-plus radiance.

```{r lights__did-function}
run_lights_did <- function(outcome_var, outcome_label, outcome_type, control_group, use_covariates, spec_label, data, transform = "log1p", min_cohort_size = min_treated_cohort_size, start_year = lights_start_year, end_year = lights_end_year) {

  n_years <- length(start_year:end_year)

  control_vars <- did_control_vars

  df <- data %>%
    filter(status == "Control" | (status == "Treated" & first_dc_year >= start_year & first_dc_year <= end_year)) %>%
    filter(year >= start_year, year <= end_year) %>%
    mutate(outcome_raw = .data[[outcome_var]]) %>%
    filter(!is.na(outcome_raw), outcome_raw >= 0)

  if (use_covariates) {
    df <- df %>% filter(if_all(all_of(control_vars), ~ !is.na(.x)))
    xformla <- did_control_formula
    covariate_label <- "Lagged ACS + race covariates"
  } else {
    xformla <- ~ 1
    covariate_label <- "No covariates"
  }

  df <- df %>%
    group_by(GEOID) %>%
    filter(n_distinct(year) == n_years) %>%
    ungroup() %>%
    mutate(G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year), 0L)) %>%
    group_by(G) %>%
    filter(G == 0 | n_distinct(GEOID) >= min_cohort_size) %>%
    ungroup() %>%
    mutate(county_id_did = as.integer(factor(GEOID)))

  if (transform == "log1p") {
    df <- df %>% mutate(outcome = log1p(outcome_raw))
    y_label <- paste0("ATT (log(1 + ", outcome_label, "))")
  } else if (transform == "log") {
    df <- df %>% filter(outcome_raw > 0) %>% mutate(outcome = log(outcome_raw))
    y_label <- paste0("ATT (log ", outcome_label, ")")
  } else if (transform == "level") {
    df <- df %>% mutate(outcome = outcome_raw)
    y_label <- paste0("ATT (", outcome_label, ")")
  } else {
    stop("transform must be one of: 'log1p', 'log', or 'level'.")
  }

  cohort_sizes <- df %>%
    filter(G > 0) %>%
    distinct(GEOID, G) %>%
    count(G, name = "n_treated_counties") %>%
    arrange(G)

  cs <- att_gt(yname = "outcome", tname = "year", idname = "county_id_did", gname = "G", xformla = xformla, control_group = control_group, clustervars = "county_id_did", allow_unbalanced_panel = TRUE, data = df)

  att_overall <- aggte(cs, type = "simple", na.rm = TRUE)
  att_dyn <- aggte(cs, type = "dynamic", na.rm = TRUE)
  att_cal <- aggte(cs, type = "calendar", na.rm = TRUE)

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    labs(title = paste("Event Study —", outcome_label), subtitle = paste0(start_year, "–", end_year, " cohorts | ", control_group, " control | ", covariate_label), x = "Years Relative to First Data Center Opening", y = y_label)

  p_calendar <- ggdid(att_cal) +
    labs(title = paste("Calendar-Time Effects —", outcome_label), subtitle = paste0(start_year, "–", end_year, " cohorts | ", control_group, " control | ", covariate_label), x = "Calendar year", y = y_label)

  list(error = FALSE, outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, transform = transform, data_used = df, cohort_sizes = cohort_sizes, cs = cs, overall = att_overall, dynamic = att_dyn, calendar = att_cal, p_event = p_event, p_calendar = p_calendar)
}

run_lights_did_safe <- function(outcome_var, outcome_label, outcome_type, control_group, use_covariates, spec_label, data) {
  tryCatch(
    run_lights_did(outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, data = data, transform = "log1p"),
    error = function(e) {
      list(error = TRUE, error_message = conditionMessage(e), outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, transform = "log1p")
    }
  )
}
```

## Section 9: Run All Light Outcome Regressions

```{r lights__run-all-did}
set.seed(12345)
all_light_did_results <- pmap(
  model_grid,
  function(outcome_var, outcome_label, outcome_type, spec_id, control_group, use_covariates, spec_label, model_id) {
    run_lights_did_safe(outcome_var = outcome_var, outcome_label = outcome_label, outcome_type = outcome_type, control_group = control_group, use_covariates = use_covariates, spec_label = spec_label, data = lights_analysis_acs)
  }
)
names(all_light_did_results) <- model_grid$model_id

# Check whether any models failed.
model_status <- tibble(model_id = names(all_light_did_results), error = map_lgl(all_light_did_results, "error"), error_message = map_chr(all_light_did_results, ~ { if (isTRUE(.x$error)) .x$error_message else "" }))

knitr::kable(model_status, caption = "Model Run Status")
```

---

## Section 10: Results Summary Table

```{r lights__results-summary}


extract_lights_results <- function(result) {
  cg   <- dplyr::recode(result$control_group,
                        "nevertreated"  = "Never Treated",
                        "notyettreated" = "Not Yet Treated")
  spec <- if (result$use_covariates) "Lagged ACS + Race Controls" else "No Covariates"

  if (isTRUE(result$error)) {
    return(tibble(Outcome = result$outcome_label, `Outcome Variable` = result$outcome_var, `Outcome Type` = result$outcome_type, Specification = spec, `Control Group` = cg, Covariates = if_else(result$use_covariates, "Yes", "No"), Transform = result$transform, ATT = NA_real_, SE = NA_real_, `95% CI Lower` = NA_real_, `95% CI Upper` = NA_real_, `p-value` = NA_real_, `Counties Used` = NA_integer_, `County-Years Used` = NA_integer_, Status = "Error", `Error Message` = result$error_message))
  }

  ATT <- result$overall$overall.att
  SE <- result$overall$overall.se
  p_value <- 2 * (1 - pnorm(abs(ATT / SE)))

  tibble(Outcome = result$outcome_label, `Outcome Variable` = result$outcome_var, `Outcome Type` = result$outcome_type, Specification = result$spec_label, `Control Group` = result$control_group, Covariates = if_else(result$use_covariates, "Yes", "No"), Transform = result$transform, ATT = ATT, SE = SE, `95% CI Lower` = ATT - 1.96 * SE, `95% CI Upper` = ATT + 1.96 * SE, `p-value` = p_value, `Counties Used` = n_distinct(result$data_used$GEOID), `County-Years Used` = nrow(result$data_used), Status = "OK", `Error Message` = "")
}

lights_results_summary <- bind_rows(lapply(all_light_did_results, extract_lights_results)) %>%
  arrange(`Outcome Variable`, Covariates, `Control Group`)

knitr::kable(lights_results_summary, digits = 3, caption = "Overall ATT Estimates for All County-Level Artificial Light at Night Outcomes")

shiny_report_dir <- here::here("ShinyApp", "report")

if (!dir.exists(shiny_report_dir)) {
  dir.create(shiny_report_dir, recursive = TRUE)
}

saveRDS(
  all_light_did_results,
  file.path(shiny_report_dir, "all_light_did_results.rds")
)
saveRDS(
  lights_results_summary,
  file.path(shiny_report_dir, "lights_results_summary.rds")
)

readr::write_csv(
  lights_results_summary,
  file.path(shiny_report_dir, "lights_results_summary.csv")
)

# Also export a copy for the Shiny app results table.
# If this Rmd is run from the repo root, ShinyApp/report is usually the correct target.
shiny_report_dir <- here("ShinyApp", "report")
if (!dir.exists(shiny_report_dir)) shiny_report_dir <- here("report")
dir.create(shiny_report_dir, showWarnings = FALSE, recursive = TRUE)
saveRDS(lights_results_summary, file.path(shiny_report_dir, "lights_results_summary.rds"))
```

## Section 11: Event Study Plots

This prints and saves event-study plots for every successful model when
`print_all_event_plots <- TRUE`.

```{r lights__event-study-plots, eval=print_all_event_plots}
for (model_id in names(all_light_did_results)) {
  res <- all_light_did_results[[model_id]]
  if (isFALSE(res$error)) {
    print(res$p_event)
    ggsave(here("figures", paste0("event_study__", model_id, ".png")), res$p_event, width = 9, height = 5, dpi = 150)
  }
}
```

## Section 12: Descriptive Summary Data for Shiny or Reporting

```{r lights__descriptive-summary-export}
lights_summary_data <- lights_analysis_acs %>%
  transmute(GEOID, county, state, year, status, first_dc_year, dc_count, nraster, rad_mean, rad_min, rad_max, rad_median, rad_sd, rad_q25, rad_q75, rad_iqr, across(all_of(did_control_vars)))

saveRDS(lights_summary_data, here("outputs", "lights_summary_data.rds"))

summary_tbl <- lights_summary_data %>%
  select(starts_with("rad_")) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "value") %>%
  filter(!is.na(value)) %>%
  group_by(Variable) %>%
  summarize(N = n(), Mean = mean(value), SD = sd(value), Min = min(value), Median = median(value), Max = max(value), .groups = "drop") %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))

knitr::kable(summary_tbl, caption = "Descriptive Summary of Light Outcomes")
```


# Part II — Data Centers & Local Economic Impact



```{r economy__setup, include=FALSE}
# Load libraries for data wrangling, spatial joins, Census API pulls, and DiD estimation.
# `did` provides att_gt/aggte/ggdid (Callaway & Sant'Anna staggered DiD).
# `callr` (used in Sections 10 and 10b) is called via callr::r() and does not need
# to be attached here.
library(knitr)
library(tidyverse)
library(sf)
library(tigris)
library(tidycensus)
library(censusapi)
library(here)
library(did)

analysis_seed <- 12345
set.seed(analysis_seed)

options(tigris_use_cache = TRUE)
Sys.setenv(CENSUS_KEY = Sys.getenv("CENSUS_KEY"))

knitr::opts_chunk$set(
  echo    = TRUE,
  tidy    = TRUE,
  tidy.opts = list(width.cutoff = 60),
  comment   = NA,
  fig.path  = "./figures/",
  fig.align = "center",
  fig.width  = 9,
  fig.height = 5,
  message = FALSE,
  warning = FALSE
)
```

## Section 1: County Boundaries

Download lower-48 county polygons from Census TIGER/Line. These are needed for the
spatial join that assigns each data center to a county.

```{r economy__county-boundaries}
non_contiguous_fips <- c("02", "15", "60", "66", "69", "72", "78")

lower_48_counties <- counties(cb = TRUE, year = 2023) %>%
  filter(!STATEFP %in% non_contiguous_fips) %>%
  st_transform(crs = 4326)
```

## Section 2: Load Data Centers

Read the cleaned data center CSV and convert to a spatial object so each facility
can be matched to the county it falls within.

```{r economy__load-datacenters}
data_centers <- read.csv(here("data", "data_final", "economyDataFinal", "clean01EconDatacenter.csv")) %>%
  filter(stage == "Operational") %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)
```

## Section 3: Treatment Assignment

```{r economy__treatment-assignment}
data_centers_county <- st_join(data_centers, lower_48_counties, join = st_within)

county_status <- data_centers_county %>%
  st_drop_geometry() %>%
  group_by(GEOID) %>%
  summarize(
    has_known_year      = any(!is.na(year_operational)),
    earliest_known_year = if_else(has_known_year, min(year_operational, na.rm = TRUE), NA_real_),
    .groups = "drop"
  ) %>%
  mutate(
    status = case_when(
      !has_known_year             ~ "Drop: Missing Years",
      earliest_known_year < 2009  ~ "Drop: Pre-2007 Only",
      earliest_known_year >= 2009 ~ "Treated"
    ),
    first_dc_year = case_when(
      status == "Treated" ~ earliest_known_year,
      TRUE                ~ NA_real_
    )
  )

mapping_data <- lower_48_counties %>%
  left_join(county_status %>% select(GEOID, status, first_dc_year), by = "GEOID") %>%
  mutate(
    status       = replace_na(status, "Control"),
    first_dc_year = replace_na(first_dc_year, NA_real_)
  )
## SAVING MAP DATA for shiny app

dc_counts <- data_centers_county %>%
  sf::st_drop_geometry() %>%
  filter(!is.na(GEOID)) %>%
  count(GEOID, name = "dc_count")

map_data_export <- mapping_data %>%
  left_join(dc_counts, by = "GEOID") %>%
  mutate(dc_count = tidyr::replace_na(dc_count, 0L)) %>%
  select(GEOID, NAMELSAD, status, first_dc_year, dc_count, geometry) %>%
  sf::st_transform(5070) %>%
  sf::st_simplify(dTolerance = 500, preserveTopology = TRUE) %>%
  sf::st_transform(4326)

saveRDS(map_data_export, "../../ShinyApp/report/map_data.rds")

dc_growth <- data_centers %>%
  sf::st_drop_geometry() %>%
  filter(!is.na(year_operational)) %>%
  count(year = as.integer(year_operational), name = "n_opened") %>%
  arrange(year) %>%
  mutate(cumulative_dcs = cumsum(n_opened))

saveRDS(dc_growth, "../../ShinyApp/report/dc_growth.rds")
```

## Section 4: Pull CBP Data
#not used anymore (for the by sector)

```{r economy__pull-cbp, cache=TRUE}
pull_cbp_year <- function(yr, naics = NULL) {
  base_vars <- c("GEO_ID", "EMP", "PAYANN", "ESTAB")
  api_args  <- list(
    name     = "cbp",
    vintage  = yr,
    vars     = base_vars,
    region   = "county:*",
    regionin = "state:*"
  )

  if (!is.null(naics)) {
    naics_var <- case_when(
      yr >= 2017 ~ "NAICS2017",
      yr >= 2012 ~ "NAICS2012",
      yr >= 2008 ~ "NAICS2007",
      TRUE       ~ "NAICS2002"
    )
    api_args[[naics_var]] <- naics
  }

  df <- tryCatch(
    do.call(getCensus, api_args),
    error = function(e) {
      message("Failed: year=", yr, " naics=", naics, ": ", e$message)
      return(NULL)
    }
  )
  if (is.null(df)) return(NULL)

  df$year        <- yr
  df$naics_group <- if (is.null(naics)) "All Industries" else paste0("NAICS ", naics)
  df
}

years <- 2003:2023

# All-industry pull
cbp_all <- bind_rows(lapply(years, pull_cbp_year, naics = NULL))

# Sector-level pulls: Information (51), Construction (23),
# Professional Services (54), Utilities (22)
naics_sectors <- c("51", "23", "54", "22")
cbp_sectors   <- bind_rows(
  lapply(naics_sectors, function(naics) bind_rows(lapply(years, pull_cbp_year, naics = naics)))
)

cbp_raw <- bind_rows(cbp_all, cbp_sectors)
```

## Section 5: Clean CBP & Inflation Adjustment

Construct county GEOIDs, deflate nominal payroll to 2017 constant dollars using
BLS CPI-U annual averages, and replace suppressed zeros with NA.

```{r economy__clean-cbp}
cbp_clean <- cbp_raw %>%
  mutate(
    GEOID  = paste0(state, county),
    EMP    = as.numeric(EMP),
    PAYANN = as.numeric(PAYANN),
    ESTAB  = as.numeric(ESTAB)
  )

# CPI-U annual averages (base year 2017 = 245.1).
# Source: BLS CPI-U, All Items, Annual Average, Series CUUR0000SA0.
cpi_u <- tibble(
  year = 2003:2023,
  cpi  = c(
    184.0, 188.9, 195.3, 201.6, 207.3, 215.3, 214.5, 218.1,
    224.9, 229.6, 233.0, 236.7, 237.0, 240.0, 245.1, 251.1,
    255.7, 258.8, 270.9, 292.7, 304.7
  )
) %>%
  mutate(deflator = 245.1 / cpi)

cbp_real <- cbp_clean %>%
  left_join(cpi_u, by = "year") %>%
  mutate(PAYANN_REAL = PAYANN * deflator)
```

---

## Section 6: Merge CBP with Treatment Status

Join treatment status onto the CBP panel. Suppressed zeros (CBP confidentiality
masking) are replaced with NA so they do not bias the log-outcome regressions.

```{r economy__merge-treatment}
analysis_counties <- mapping_data %>%
  st_drop_geometry() %>%
  filter(status %in% c("Treated", "Control")) %>%
  select(GEOID, status, first_dc_year)

cbp_analysis <- cbp_real %>%
  left_join(analysis_counties, by = "GEOID") %>%
  filter(!is.na(status)) %>%
  mutate(
    EMP         = if_else(EMP == 0,         NA_real_, EMP),
    PAYANN      = if_else(PAYANN == 0,      NA_real_, PAYANN),
    PAYANN_REAL = if_else(PAYANN_REAL == 0, NA_real_, PAYANN_REAL),
    ESTAB       = if_else(ESTAB == 0,       NA_real_, ESTAB)
  )
```

## Section 7: Pull ACS Data

Pull ACS 5-year estimates for 2009–2023.

```{r economy__pull-acs, cache=TRUE}
acs_years <- 2009:2023

pull_acs_year <- function(yr) {
  # Sector employment codes (DP03_0033-0045) are stable across all years in this range,
  # so they're pulled unconditionally rather than inside the <=2018 branch.
  sector_vars <- c(
    emp_agriculture   = "DP03_0033",
    emp_construction  = "DP03_0034",
    emp_manufacturing = "DP03_0035",
    emp_wholesale     = "DP03_0036",
    emp_retail        = "DP03_0037",
    emp_transport     = "DP03_0038",
    emp_information   = "DP03_0039",
    emp_finance       = "DP03_0040",
    emp_professional  = "DP03_0041",
    emp_education     = "DP03_0042",
    emp_arts          = "DP03_0043",
    emp_other         = "DP03_0044",
    emp_public        = "DP03_0045"
  )

  base_vars <- c(
    median_income = "DP03_0062",
    unemployment_rate = "DP03_0009P",
    labor_force_participation = "DP03_0004P",
    poverty_rate = "DP03_0119P",
    pct_bachelors = if (yr <= 2018) "DP02_0061P" else "DP02_0062P",
    pct_hs_grad   = if (yr <= 2018) "DP02_0067P" else "DP02_0068P",
    total_pop = "B01003_001"
  )

  vars <- c(base_vars, sector_vars)

  get_acs(geography = "county", variables = vars, year = yr, survey = "acs5") %>% mutate(year = yr)
}

acs_raw <- bind_rows(lapply(acs_years, pull_acs_year))

acs_covariates <- acs_raw %>%
  select(GEOID, year, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate) %>%
  mutate(
    log_pop = log(total_pop),
    log_median_income = log(median_income)
  )

# Read County Health files.
# Income variables become additional ACS-style outcomes.
# Race variables become additional covariates, then are lagged below.
migration_economy <- map_dfr(acs_years, function(yr) {
  readxl::read_excel(
    here("data", "economyData", "raw_migration", paste0("clh_", yr, "_county_2_0.xlsx")),
    sheet = "Data",
    col_types = "text"
  ) %>%
    transmute(
      GEOID = COUNTYFIPS,
      year = as.integer(YEAR),
      ACS_MEDIAN_INC_F = as.numeric(ACS_MEDIAN_INC_F),
      ACS_MEDIAN_INC_M = as.numeric(ACS_MEDIAN_INC_M),
      ACS_PER_CAPITA_INC = as.numeric(ACS_PER_CAPITA_INC),
      ACS_PCT_WHITE = as.numeric(ACS_PCT_WHITE),
      ACS_PCT_BLACK = as.numeric(ACS_PCT_BLACK),
      ACS_PCT_HISPANIC = as.numeric(ACS_PCT_HISPANIC),
      ACS_PCT_ASIAN = as.numeric(ACS_PCT_ASIAN),
      ACS_PCT_AIAN = as.numeric(ACS_PCT_AIAN)
    )
}) %>%
  mutate(
    log_median_inc_f = log(ACS_MEDIAN_INC_F),
    log_median_inc_m = log(ACS_MEDIAN_INC_M),
    log_per_capita_inc = log(ACS_PER_CAPITA_INC)
  )

cbp_analysis_acs <- cbp_analysis %>%
  left_join(acs_covariates, by = c("GEOID", "year")) %>%
  left_join(migration_economy, by = c("GEOID", "year")) %>%
  filter(year >= 2009)

# Build one-year lagged controls.
cbp_analysis_acs <- cbp_analysis_acs %>%
  arrange(GEOID, naics_group, year) %>%
  group_by(GEOID, naics_group) %>%
  mutate(
    lag_log_pop = lag(log_pop),
    lag_log_median_income = lag(log_median_income),
    lag_pct_bachelors = lag(pct_bachelors),
    lag_pct_hs_grad = lag(pct_hs_grad),
    lag_pct_white = lag(ACS_PCT_WHITE),
    lag_pct_black = lag(ACS_PCT_BLACK),
    lag_pct_hispanic = lag(ACS_PCT_HISPANIC),
    lag_pct_asian = lag(ACS_PCT_ASIAN),
    lag_pct_aian = lag(ACS_PCT_AIAN)
  ) %>%
  ungroup()
```

## Section 8: Define Outcome Lists

```{r economy__outcome-lists}
# All-industry CBP outcomes
outcomes_cbp <- list(
  list(var = "EMP",         label = "Employment"),
  list(var = "PAYANN_REAL", label = "Real Annual Payroll (2017 $)"),
  list(var = "ESTAB",       label = "Establishments")
)

# ACS sector employment outcomes (DP03_0033-0045)
outcomes_acs_sector <- list(
  list(var = "emp_agriculture",   label = "Employment — Agriculture, Forestry, Fishing, Hunting, Mining"),
  list(var = "emp_construction",  label = "Employment — Construction"),
  list(var = "emp_manufacturing", label = "Employment — Manufacturing"),
  list(var = "emp_wholesale",     label = "Employment — Wholesale Trade"),
  list(var = "emp_retail",        label = "Employment — Retail Trade"),
  list(var = "emp_transport",     label = "Employment — Transportation, Warehousing, Utilities"),
  list(var = "emp_information",   label = "Employment — Information"),
  list(var = "emp_finance",       label = "Employment — Finance, Insurance, Real Estate"),
  list(var = "emp_professional",  label = "Employment — Professional, Scientific, Management, Admin"),
  list(var = "emp_education",     label = "Employment — Educational, Health Care, Social Assistance"),
  list(var = "emp_arts",          label = "Employment — Arts, Entertainment, Recreation, Food Services"),
  list(var = "emp_other",         label = "Employment — Other Services"),
  list(var = "emp_public",        label = "Employment — Public Administration")
)

# ACS outcomes. The rate outcomes (unemployment, LFP) are levels; the income and
# population outcomes are already logged in Section 7, so no further log transform
# is applied in the DiD (Section 12).
outcomes_acs <- list(
  list(var = "unemployment_rate", label = "Unemployment Rate"),
  list(var = "labor_force_participation", label = "Labor Force Participation Rate"),
  list(var = "log_median_income", label = "Log Median Household Income"),
  list(var = "log_pop", label = "Log Population"),
  list(var = "log_median_inc_f", label = "Log Median Income — Female"),
  list(var = "log_median_inc_m", label = "Log Median Income — Male"),
  list(var = "log_per_capita_inc", label = "Log Per Capita Income")
)
```

## Section 9: DiD — All Industries, Never-Treated Control

Baseline staggered DiD (Callaway & Sant'Anna) on all-industry CBP outcomes, using
never-treated counties as the control group and no additional covariates. The
regression window is 2009–2023, matching the ACS-controlled models so the
specifications are comparable. Cohorts are defined by first data-center opening year
(`G = first_dc_year - 2008`); never-treated counties get `G = 0`.

```{r economy__did-baseline}
run_did <- function(outcome_var, outcome_label, naics_filter = "All Industries", data) {

  df <- data %>%
    filter(naics_group == naics_filter) %>%
    filter(
      status == "Control" |
        (status == "Treated" &
           first_dc_year >= 2009 &
           first_dc_year <= 2023)
    ) %>%
    filter(year >= 2009, year <= 2023) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    mutate(
      county_id = as.integer(factor(GEOID)),
      G = if_else(
        status == "Treated" & !is.na(first_dc_year),
        as.integer(first_dc_year) - 2008,
        0L
      ),
      outcome = log(.data[[outcome_var]]),
      year2 = year - 2008
    )

  cs <- att_gt(
    yname = "outcome",
    tname = "year2",
    idname = "county_id",
    gname = "G",
    xformla = ~ 1,
    control_group = "nevertreated",
    clustervars = "county_id",
    data = df
  )

  att_overall <- aggte(cs, type = "simple", na.rm = TRUE)
  att_dyn <- aggte(cs, type = "dynamic", na.rm = TRUE)

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    labs(
      title = paste("Event Study —", outcome_label),
      subtitle = "2009–2023 cohorts | Never-treated control | No covariates",
      x = "Years Relative to First Data Center Opening",
      y = paste0("ATT (log ", outcome_label, ")")
    )

  list(
    label = outcome_label,
    cs = cs,
    overall = att_overall,
    dynamic = att_dyn,
    p_event = p_event
  )
}

set.seed(analysis_seed)

did_results <- lapply(
  outcomes_cbp,
  function(o) run_did(
    outcome_var = o$var,
    outcome_label = o$label,
    data = cbp_analysis
  )
)

names(did_results) <- c("employment", "payroll", "establishments")

did_results$employment$p_event
did_results$payroll$p_event
did_results$establishments$p_event

summary(did_results$employment$overall)
summary(did_results$payroll$overall)
summary(did_results$establishments$overall)
```

## Section 10: DiD — ACS Sector Employment, No Covariates


```{r economy__did-sector-nocov}
run_sector_did_acs <- function(outcome_var, outcome_label, control_group, data) {

  df <- data %>%
    filter(
      status == "Control" |
        (status == "Treated" & first_dc_year >= 2009 & first_dc_year <= 2023)
    ) %>%
    filter(year >= 2009, year <= 2023) %>%
    # ACS sector vars are repeated across the CBP naics_group rows for a county-year.
    # Keep one row per county-year. "All Industries" sorts first (Section 7 arrange),
    # so its row is the one retained.
    distinct(GEOID, year, .keep_all = TRUE) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    group_by(GEOID) %>%
    filter(n() == length(2009:2023)) %>%   # balanced panel; drops singletons that crash att_gt
    ungroup() %>%
    mutate(
      county_id = as.integer(factor(GEOID)),
      G = if_else(
        status == "Treated" & !is.na(first_dc_year),
        as.integer(first_dc_year) - 2008,
        0L
      ),
      outcome = log(.data[[outcome_var]]),
      year2   = year - 2008
    )

  cs <- att_gt(
    yname = "outcome", tname = "year2", idname = "county_id", gname = "G",
    xformla = ~ 1,
    control_group = control_group,
    clustervars = "county_id",
    data = df
    # base period left at default (varying) to match Sections 9/11/12
  )

  att_overall <- aggte(cs, type = "simple", na.rm = TRUE)
  att_dyn     <- aggte(cs, type = "dynamic", na.rm = TRUE)

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    labs(
      title = paste("Event Study —", outcome_label),
      subtitle = paste("2009–2023 cohorts |", control_group, "control | No covariates"),
      x = "Years Relative to First Data Center Opening",
      y = paste0("ATT (log ", outcome_label, ")")
    )

  list(label = outcome_label, control_group = control_group,
       cs = cs, overall = att_overall, dynamic = att_dyn, p_event = p_event)
}

# Child-process wrapper: attach packages inside the subprocess so it's self-sufficient.
safe_sector <- function(outcome_var, outcome_label, control_group, data, seed = 12345) {
  callr::r(
    function(fn, outcome_var, outcome_label, control_group, data, seed) {
      library(dplyr)
      library(ggplot2)
      library(did)
      set.seed(seed)
      fn(outcome_var, outcome_label, control_group, data)
    },
    args = list(run_sector_did_acs, outcome_var, outcome_label, control_group, data, seed),
    error = "error"
  )
}

did_acs_sector_results_nt <- Map(
  function(o, i) safe_sector(o$var, o$label, "nevertreated", cbp_analysis_acs, seed = analysis_seed + i),
  outcomes_acs_sector,
  seq_along(outcomes_acs_sector)
)

did_acs_sector_results_nyt <- Map(
  function(o, i) safe_sector(o$var, o$label, "notyettreated", cbp_analysis_acs, seed = analysis_seed + 100 + i),
  outcomes_acs_sector,
  seq_along(outcomes_acs_sector)
)

sector_names <- sub("^emp_", "", vapply(outcomes_acs_sector, `[[`, "", "var"))
names(did_acs_sector_results_nt)  <- sector_names
names(did_acs_sector_results_nyt) <- sector_names

sapply(sector_names, function(s) {
  r <- did_acs_sector_results_nt[[s]]
  if (inherits(r, "error")) NA_integer_ else length(unique(r$cs$DIDparams$data$county_id))
})


#debugging 


# It prints the stored $p_event, falling back to rebuilding parent-side from the
# serialized $dynamic (aggte) object if the stored ggplot fails to print.
print_sector_event <- function(res, control_label) {
  if (inherits(res, "error")) {
    message("Skipping ", control_label, " — sector errored in subprocess.")
    return(invisible(NULL))
  }
  p <- tryCatch(
    print(res$p_event),
    error = function(e) {
      rebuilt <- ggdid(res$dynamic) +
        geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
        labs(
          title = paste("Event Study —", res$label),
          subtitle = paste("2009–2023 cohorts |", res$control_group, "control"),
          x = "Years Relative to First Data Center Opening",
          y = paste0("ATT (log ", res$label, ")")
        )
      print(rebuilt)
    }
  )
  invisible(p)
}

# Never-treated event studies
for (s in sector_names) {
  print_sector_event(did_acs_sector_results_nt[[s]], "Never Treated")
}

# Not-yet-treated event studies
for (s in sector_names) {
  print_sector_event(did_acs_sector_results_nyt[[s]], "Not Yet Treated")
}
```


## Section 10b: DiD — ACS Sector Employment, Lagged ACS + Race Controls

Covariate-controlled copy of Section 10: the same per-sector, two-control-group DiD,
but with the Section 11/12 lagged controls added to `xformla` (log population, log
median income, bachelor's and HS-grad shares, and five race shares).

```{r economy__did-sector-cov}
run_sector_did_acs_cov <- function(outcome_var, outcome_label, control_group, data,
                                   min_cohort_size = 5) {

  df <- data %>%
    filter(
      status == "Control" |
        (status == "Treated" & first_dc_year >= 2009 & first_dc_year <= 2023)
    ) %>%
    filter(year >= 2009, year <= 2023) %>%
    # Keep one row per county-year ("All Industries" sorts first; see Section 10).
    distinct(GEOID, year, .keep_all = TRUE) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    filter(
      !is.na(lag_log_pop), !is.na(lag_log_median_income),
      !is.na(lag_pct_bachelors), !is.na(lag_pct_hs_grad),
      !is.na(lag_pct_white), !is.na(lag_pct_black),
      !is.na(lag_pct_hispanic), !is.na(lag_pct_asian), !is.na(lag_pct_aian)
    ) %>%
    group_by(GEOID) %>%
    filter(n() >= 2) %>%              # singleton guard: prevents the att_gt segfault
    
    # Note: why this filter?
    #All these models use att_gt() to compare counties over time. To measure change over time, a county has to show up in at least two different years. If a county appears in only one year, att_gt() breaks. It crashed the whole R session instead of just giving an error message. So we have to remove those single-year counties before running the model.
                                                                                   
    ungroup() %>%
    mutate(
      G = if_else(
        status == "Treated" & !is.na(first_dc_year),
        as.integer(first_dc_year) - 2008,
        0L
      ),
      outcome = log(.data[[outcome_var]]),
      year2   = year - 2008
    ) %>%
    # Drop treated cohorts too small to estimate after covariate filtering.
    # n_distinct(GEOID) counts counties (not county-years). Controls (G == 0) kept.
    group_by(G) %>%
    filter(G == 0 | n_distinct(GEOID) >= min_cohort_size) %>%
    ungroup() %>%
    # Assign county_id AFTER all row filtering so the factor levels have no gaps.
    mutate(county_id = as.integer(factor(GEOID)))

  cs <- att_gt(
    yname = "outcome", tname = "year2", idname = "county_id", gname = "G",
    xformla = ~ lag_log_pop + lag_log_median_income + lag_pct_bachelors +
      lag_pct_hs_grad + lag_pct_white + lag_pct_black +
      lag_pct_hispanic + lag_pct_asian + lag_pct_aian,
    control_group = control_group,
    clustervars = "county_id",
    data = df
  )

  att_overall <- aggte(cs, type = "simple", na.rm = TRUE)
  att_dyn     <- aggte(cs, type = "dynamic", na.rm = TRUE)

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    labs(
      title = paste("ACS-Controlled Event Study —", outcome_label),
      subtitle = paste("2009–2023 cohorts |", control_group,
                       "control | Lagged ACS + race controls"),
      x = "Years Relative to First Data Center Opening",
      y = paste0("ATT (log ", outcome_label, ")")
    )

  list(label = outcome_label, control_group = control_group,
       cs = cs, overall = att_overall, dynamic = att_dyn, p_event = p_event)
}

# Child-process wrapper (same pattern as Section 10).
safe_sector_cov <- function(outcome_var, outcome_label, control_group, data, seed = 12345) {
  callr::r(
    function(fn, outcome_var, outcome_label, control_group, data, seed) {
      library(dplyr)
      library(ggplot2)
      library(did)
      set.seed(seed)
      fn(outcome_var, outcome_label, control_group, data)
    },
    args = list(run_sector_did_acs_cov, outcome_var, outcome_label, control_group, data, seed),
    error = "error"
  )
}

did_acs_sector_cov_results_nt <- Map(
  function(o, i) safe_sector_cov(o$var, o$label, "nevertreated", cbp_analysis_acs, seed = analysis_seed + 200 + i),
  outcomes_acs_sector,
  seq_along(outcomes_acs_sector)
)

did_acs_sector_cov_results_nyt <- Map(
  function(o, i) safe_sector_cov(o$var, o$label, "notyettreated", cbp_analysis_acs, seed = analysis_seed + 300 + i),
  outcomes_acs_sector,
  seq_along(outcomes_acs_sector)
)

names(did_acs_sector_cov_results_nt)  <- sector_names
names(did_acs_sector_cov_results_nyt) <- sector_names

# Retained-county check. Expect lower counts than Section 10 (covariate NA filtering
# + the 2009 lag drop + dropped small cohorts). NA = errored subprocess.
sapply(sector_names, function(s) {
  r <- did_acs_sector_cov_results_nt[[s]]
  if (inherits(r, "error")) NA_integer_ else length(unique(r$cs$DIDparams$data$county_id))
})

for (s in sector_names) {
  print_sector_event(did_acs_sector_cov_results_nt[[s]],  "Never Treated")
}
for (s in sector_names) {
  print_sector_event(did_acs_sector_cov_results_nyt[[s]], "Not Yet Treated")
}
```



## Section 11: DiD — All Industries, ACS Controls, Not-Yet-Treated Control

```{r economy__did-acs-notyettreated}
run_did_acs_nyt <- function(outcome_var, outcome_label, data) {
  df <- data %>%
    filter(naics_group == "All Industries") %>%
    filter(status == "Control" | (status == "Treated" & first_dc_year >= 2009 & first_dc_year <= 2023)) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    filter(
      !is.na(lag_log_pop), !is.na(lag_log_median_income), !is.na(lag_pct_bachelors), !is.na(lag_pct_hs_grad), !is.na(lag_pct_white), !is.na(lag_pct_black), !is.na(lag_pct_hispanic), !is.na(lag_pct_asian), !is.na(lag_pct_aian)) %>%
    mutate(
      county_id = as.integer(factor(GEOID)),
      G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year) - 2008, 0L),
      outcome = log(.data[[outcome_var]]),
      year2 = year - 2008
    ) #%>%
    #group_by(G) %>%
    #filter(G == 0 | n_distinct(GEOID) >= 10) %>%   # drop tiny treated cohorts; keep all controls
    #ungroup() %>%
    #mutate(county_id = as.integer(factor(GEOID))) 

  cs <- att_gt(
    yname = "outcome",
    tname = "year2",
    idname = "county_id",
    gname = "G",
    xformla = ~ lag_log_pop + lag_log_median_income + lag_pct_bachelors + lag_pct_hs_grad + lag_pct_white + lag_pct_black + lag_pct_hispanic + lag_pct_asian + lag_pct_aian,
    control_group = "notyettreated",
    clustervars = "county_id",
    data = df
  )

  att_overall <- aggte(cs, type = "simple", na.rm = TRUE)
  att_dyn <- aggte(cs, type = "dynamic", na.rm = TRUE)

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    coord_cartesian(ylim = c(-0.2, 0.25)) +
    labs(
      title = paste("ACS-Controlled Event Study —", outcome_label),
      subtitle = "2009–2023 cohorts | Not-yet-treated control | Lagged ACS + race controls",
      x = "Years Relative to First Data Center Opening",
      y = paste0("ATT (log ", outcome_label, ")")
    )

  list(label = outcome_label, cs = cs, overall = att_overall, dynamic = att_dyn, p_event = p_event)
}
set.seed(analysis_seed + 300)

did_results_acs_nyt <- lapply(outcomes_cbp, function(o) run_did_acs_nyt(outcome_var = o$var, outcome_label = o$label, data = cbp_analysis_acs))

names(did_results_acs_nyt) <- c("employment", "payroll", "establishments")

did_results_acs_nyt$employment$p_event
did_results_acs_nyt$payroll$p_event
did_results_acs_nyt$establishments$p_event
```

## Section 12: DiD — ACS Outcomes

```{r economy__did-acs-outcomes}
run_did_acs_outcome <- function(outcome_var, outcome_label, control_group, data) {
  df <- data %>%
    filter(naics_group == "All Industries") %>%
    filter(status == "Control" | (status == "Treated" & first_dc_year >= 2009 & first_dc_year <= 2023)) %>%
    filter(!is.na(.data[[outcome_var]]), .data[[outcome_var]] > 0) %>%
    filter(
      !is.na(lag_log_pop), !is.na(lag_log_median_income), !is.na(lag_pct_bachelors), !is.na(lag_pct_hs_grad), !is.na(lag_pct_white), !is.na(lag_pct_black), !is.na(lag_pct_hispanic), !is.na(lag_pct_asian), !is.na(lag_pct_aian)) %>%
    mutate(
      county_id = as.integer(factor(GEOID)),
      G = if_else(status == "Treated" & !is.na(first_dc_year), as.integer(first_dc_year) - 2008, 0L),
      outcome = .data[[outcome_var]],
      year2 = year - 2008
    )

  cs <- att_gt(
    yname = "outcome",
    tname = "year2",
    idname = "county_id",
    gname = "G",
    xformla = ~ lag_log_pop + lag_log_median_income + lag_pct_bachelors + lag_pct_hs_grad + lag_pct_white + lag_pct_black + lag_pct_hispanic + lag_pct_asian + lag_pct_aian,
    control_group = control_group,
    clustervars = "county_id",
    data = df
  )

  att_overall <- aggte(cs, type = "simple", na.rm = TRUE)
  att_dyn <- aggte(cs, type = "dynamic", na.rm = TRUE)

  p_event <- ggdid(att_dyn) +
    geom_vline(xintercept = -0.5, linetype = "dashed", color = "red") +
    labs(
      title = paste("Event Study —", outcome_label),
      subtitle = paste("2009–2023 cohorts |", control_group, "control | Lagged ACS + race controls"),
      x = "Years Relative to First Data Center Opening",
      y = paste0("ATT (", outcome_label, ")")
    )

  list(label = outcome_label, cs = cs, overall = att_overall, dynamic = att_dyn, p_event = p_event)
}

set.seed(analysis_seed + 400)

did_results_acs_outcomes_nt <- lapply(
  outcomes_acs,
  function(o) run_did_acs_outcome(outcome_var = o$var, outcome_label = o$label, control_group = "nevertreated", data = cbp_analysis_acs)
)

names(did_results_acs_outcomes_nt) <- c("unemployment", "labor_force_participation", "log_income", "log_pop", "female_income", "male_income", "per_capita_income")

set.seed(analysis_seed + 500)

did_results_acs_outcomes_nyt <- lapply(
  outcomes_acs,
  function(o) run_did_acs_outcome(outcome_var = o$var, outcome_label = o$label, control_group = "notyettreated", data = cbp_analysis_acs)
)

names(did_results_acs_outcomes_nyt) <- c("unemployment", "labor_force_participation", "log_income", "log_pop", "female_income", "male_income", "per_capita_income")

# Never-treated plots
did_results_acs_outcomes_nt$unemployment$p_event
did_results_acs_outcomes_nt$labor_force_participation$p_event
did_results_acs_outcomes_nt$log_income$p_event
did_results_acs_outcomes_nt$log_pop$p_event
did_results_acs_outcomes_nt$female_income$p_event
did_results_acs_outcomes_nt$male_income$p_event
did_results_acs_outcomes_nt$per_capita_income$p_event

# Not-yet-treated plots
did_results_acs_outcomes_nyt$unemployment$p_event
did_results_acs_outcomes_nyt$labor_force_participation$p_event
did_results_acs_outcomes_nyt$log_income$p_event
did_results_acs_outcomes_nyt$log_pop$p_event
did_results_acs_outcomes_nyt$female_income$p_event
did_results_acs_outcomes_nyt$male_income$p_event
did_results_acs_outcomes_nyt$per_capita_income$p_event
```


## Section 13: Results Summary Tables


```{r economy__results-summary}
extract_results <- function(result, outcome, control_group) {

  ATT <- result$overall$overall.att
  SE  <- result$overall$overall.se

  p_value <- 2 * (1 - pnorm(abs(ATT / SE)))

  tibble(
    Outcome = outcome,
    `Control Group` = control_group,
    ATT = ATT,
    SE = SE,
    `95% CI Lower` = ATT - 1.96 * SE,
    `95% CI Upper` = ATT + 1.96 * SE,
    `p-value` = p_value
  )
}

# -----------------------------
# Table 1: CBP outcomes — Section 9 (never-treated, no covariates)
# -----------------------------
cbp_summary_nt <- bind_rows(
  Map(
    function(result, outcome_info) {
      extract_results(result, outcome_info$label, "Never Treated")
    },
    did_results, outcomes_cbp
  )
)

knitr::kable(cbp_summary_nt, digits = 3,
  caption = "Table 1. Overall ATT Estimates for CBP Outcomes")

# -----------------------------
# Table 2: CBP outcomes with ACS controls — Section 11 (not-yet-treated)
# -----------------------------
cbp_summary_acs_nyt <- bind_rows(
  Map(
    function(result, outcome_info) {
      extract_results(result, outcome_info$label, "Not Yet Treated")  # was "Not Yet Treated + ACS Controls"
    },
    did_results_acs_nyt, outcomes_cbp
  )
)

knitr::kable(cbp_summary_acs_nyt, digits = 3,
  caption = "Table 2. Overall ATT Estimates for CBP Outcomes with ACS Controls")

# -----------------------------
# Table 3: ACS outcomes — Section 12 (never- and not-yet-treated)
# -----------------------------
acs_summary_nt <- bind_rows(
  Map(
    function(result, outcome_info) extract_results(result, outcome_info$label, "Never Treated"),
    did_results_acs_outcomes_nt, outcomes_acs
  )
)

acs_summary_nyt <- bind_rows(
  Map(
    function(result, outcome_info) extract_results(result, outcome_info$label, "Not Yet Treated"),
    did_results_acs_outcomes_nyt, outcomes_acs
  )
)

acs_summary <- bind_rows(acs_summary_nt, acs_summary_nyt)

knitr::kable(acs_summary, digits = 3,
  caption = "Table 3. Overall ATT Estimates for ACS Outcomes")

# Main export: CBP (ACS-controlled) + ACS outcomes.
results_summary <- bind_rows(
  cbp_summary_nt %>%                                    # Section 9 baseline (no covariates)
    mutate(Specification = "No Covariates", .after = `Control Group`),
  cbp_summary_acs_nyt %>%                               # Section 11
    mutate(Specification = "Lagged ACS + Race Controls", .after = `Control Group`),
  acs_summary %>%                                       # Section 12
    mutate(Specification = "Lagged ACS + Race Controls", .after = `Control Group`)
)

saveRDS(results_summary, file = "../../ShinyApp/report/results_summary.rds")

# -----------------------------
# Tables 4 & 5: ACS sector employment outcomes — Sections 10 and 10b
# Kept in their own object/export, tagged by Specification, for the Shiny
# sector table. extract_sector guards callr error objects (returns NULL, which
# bind_rows drops) so a partial failure yields a shorter table rather than an error.
# -----------------------------
extract_sector <- function(results_list, control_label, spec_label) {
  bind_rows(Map(
    function(res, o) {
      if (inherits(res, "error")) return(NULL)
      extract_results(res, o$label, control_label) %>%
        mutate(Specification = spec_label, .after = `Control Group`)
    },
    results_list, outcomes_acs_sector
  ))
}

# Table 4: no-covariate sector results (Section 10)
sector_summary_nocov <- bind_rows(
  extract_sector(did_acs_sector_results_nt,  "Never Treated",   "No Covariates"),
  extract_sector(did_acs_sector_results_nyt, "Not Yet Treated", "No Covariates")
)

knitr::kable(sector_summary_nocov, digits = 3,
  caption = "Table 4. Overall ATT — ACS Sector Employment (No Covariates)")

# Table 5: covariate-controlled sector results (Section 10b)
sector_summary_cov <- bind_rows(
  extract_sector(did_acs_sector_cov_results_nt,  "Never Treated",   "Lagged ACS + Race Controls"),
  extract_sector(did_acs_sector_cov_results_nyt, "Not Yet Treated", "Lagged ACS + Race Controls")
)

knitr::kable(sector_summary_cov, digits = 3,
  caption = "Table 5. Overall ATT — ACS Sector Employment (Lagged ACS + Race Controls)")

# Combined sector export: both specifications in one tidy table for Shiny.
sector_summary <- bind_rows(sector_summary_nocov, sector_summary_cov)

saveRDS(sector_summary, file = "../../ShinyApp/report/sector_summary.rds")
```

######################################
##SECTION 14: 

#Model summary 

```{r economy__chunk_16}

## Section 14: Export event-study plots for the Shiny app
dir.create("../../ShinyApp/www/event_studies", recursive = TRUE, showWarnings = FALSE)

es_index <- list()

save_event <- function(res, control, spec, source) {
  if (is.null(res) || inherits(res, "error")) return(invisible(NULL))
  p <- tryCatch(res$p_event, error = function(e) NULL)
  if (is.null(p))
    p <- tryCatch(did::ggdid(res$dynamic), error = function(e) NULL)
  if (is.null(p)) return(invisible(NULL))

  outcome <- res$label
  fname <- paste0("es_",
                  gsub("[^A-Za-z0-9]+", "_", paste(source, outcome, control, spec)),
                  ".png")
  ggplot2::ggsave(file.path("../../ShinyApp/www/event_studies", fname),
                  plot = p, width = 9, height = 5, dpi = 110, bg = "white")

  es_index[[length(es_index) + 1]] <<- tibble::tibble(
    Outcome = outcome, `Control Group` = control,
    Specification = spec, Source = source, file = fname
  )
}

for (r in did_results)                    save_event(r, "Never Treated",   "No Covariates",              "Main")
for (r in did_results_acs_nyt)            save_event(r, "Not Yet Treated", "Lagged ACS + Race Controls", "Main")
for (r in did_results_acs_outcomes_nt)    save_event(r, "Never Treated",   "Lagged ACS + Race Controls", "Main")
for (r in did_results_acs_outcomes_nyt)   save_event(r, "Not Yet Treated", "Lagged ACS + Race Controls", "Main")
for (r in did_acs_sector_results_nt)      save_event(r, "Never Treated",   "No Covariates",              "Sector")
for (r in did_acs_sector_results_nyt)     save_event(r, "Not Yet Treated", "No Covariates",              "Sector")
for (r in did_acs_sector_cov_results_nt)  save_event(r, "Never Treated",   "Lagged ACS + Race Controls", "Sector")
for (r in did_acs_sector_cov_results_nyt) save_event(r, "Not Yet Treated", "Lagged ACS + Race Controls", "Sector")

saveRDS(dplyr::bind_rows(es_index), "../../ShinyApp/report/event_study_index.rds")

#####################################

library(dplyr)
library(tidyr)
library(ggplot2)

sumdat_src <- cbp_analysis_acs
if (inherits(sumdat_src, "sf")) sumdat_src <- sf::st_drop_geometry(sumdat_src)

sumdat1 <- sumdat_src %>%
  filter(naics_group == "All Industries") %>%
  transmute(
    status, year,
    Employment                    = EMP,
    `Real Payroll (2017$)`        = PAYANN_REAL,
    Establishments                = ESTAB,
    `Unemployment Rate`           = unemployment_rate,
    `Labor Force Part. (%)`       = labor_force_participation,
    `Median HH Income`            = median_income,
    Population                    = total_pop,
    `% Bachelor's+`               = pct_bachelors,
    `% HS Grad+`                  = pct_hs_grad,
    `Median Income (Female)`      = ACS_MEDIAN_INC_F,
    `Median Income (Male)`        = ACS_MEDIAN_INC_M,
    `Per Capita Income`           = ACS_PER_CAPITA_INC,
    `% White`                     = ACS_PCT_WHITE,
    `% Black`                     = ACS_PCT_BLACK,
    `% Hispanic`                  = ACS_PCT_HISPANIC,
    `% Asian`                     = ACS_PCT_ASIAN,
    `% AIAN`                      = ACS_PCT_AIAN,
    `Emp (Agriculture/Mining)`    = emp_agriculture,
    `Emp (Construction)`          = emp_construction,
    `Emp (Manufacturing)`         = emp_manufacturing,
    `Emp (Wholesale Trade)`       = emp_wholesale,
    `Emp (Retail Trade)`          = emp_retail,
    `Emp (Transport/Utilities)`   = emp_transport,
    `Emp (Information)`           = emp_information,
    `Emp (Finance/Real Estate)`   = emp_finance,
    `Emp (Professional/Admin)`    = emp_professional,
    `Emp (Education/Health)`      = emp_education,
    `Emp (Arts/Food Services)`    = emp_arts,
    `Emp (Other Services)`        = emp_other,
    `Emp (Public Administration)` = emp_public
  )

saveRDS(sumdat1, "../../ShinyApp/report/economy_summary_data.rds")

summary_tbl <- sumdat1 %>%
  select(-status, -year) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "value") %>%
  filter(!is.na(value)) %>%
  group_by(Variable) %>%
  summarise(
    N = n(), Mean = mean(value), SD = sd(value),
    Min = min(value), Median = median(value), Max = max(value),
    .groups = "drop"
  ) %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))

# taller table now
tbl_plot <- gridExtra::tableGrob(summary_tbl, rows = NULL)
ggsave("../../ShinyApp/www/economy_summary_table.png",
       plot = tbl_plot, width = 9,
       height = 0.28 * nrow(summary_tbl) + 1, dpi = 150, bg = "white")
```


